### 2021-09-05 report/10-introduction.tex
Add README, .gitignore, & .tex files for report

\chapter{Introduction} \label{chapter:Introduction}
\section{Theory}
Here the basic principles behind the project should be explained and any relevant theory given. The present work should be put into perspective in relation to previous investigations and references to these should be included.
\section{Sample text}
\blindtext
\blindtext
\subsection{Sample text in detail}
\blindtext
\blindtext
\blindtext
\section{Another section with lots of sample text}
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext
\blindtext

### 2021-09-05 report/report.tex
Add README, .gitignore, & .tex files for report

\documentclass[sotoncolour]{uosthesis}  % Use the Thesis Style with custom link colour
\graphicspath{{../figures/}}            % Location of your graphics files
\usepackage[round]{natbib}              % Use Natbib style for the refs.
\usepackage{bibentry}                   % Use bibentry for prepublished works
\nobibliography*                        % Use bibentry for prepublished works
\usepackage{attrib}                     % Use the attrib package for quotations
\hypersetup{colorlinks=true}            % Set to false for black/white printing
\hypersetup{pdfstartpage=1}             % Set first page to skip copyright declaration

\usepackage{blindtext}                  % TODO: removeme

%% ----------------------------------------------------------------
%% --------------------THESIS/DOC INFORMATION ---------------------
%\faculty     {Faculty of Science}
%\FACULTY     {\MakeUppercase{\facname}}
\department  {School of Physics and Astronomy}
\DEPARTMENT  {\MakeUppercase{\deptname}}
%\group       {[Group name]}
%\GROUP       {\MakeUppercase{\groupname}}
\title       {BSc Project Report}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
%% ------------------ FRONT MATTER ORGANISATION -------------------
\pagenumbering{gobble} % removes page number
\raggedright           % Set the style to left justification, remove for fill justification

\frontmatter
\maketitle
\begin{abstract}
\input{00-abstract}
\end{abstract}
\pdfbookmark[0]{\contentsname}{toc} % Add pdf bookmark for contents page for navigation
\tableofcontents
\listoffigures
\listoftables
\addtotoc{Listings} % The list of listings does not, by default, appear in the ToC
\lstlistoflistings
\listofaddmaterial
\mainmatter
%% ------------------ MAIN MATTER (CONTENT) --------------------
\input{10-introduction}
\input{30-experiment}
\input{50-results}
\input{70-conclusions}

\appendix
\input{90-appendix-a}
\backmatter
\bibliographystyle{plainnat}
\bibliography{references}
\chapter{Bibliography}
To use bibliography as well as the references section use the \texttt{multibbl} package.
\end{document}
%% ----------------------------------------------------------------

### 2021-09-05 article/article.tex
Add article .tex files

--- 2021-09-05 report/report.tex
@@
-\documentclass[sotoncolour]{uosthesis}  % Use the Thesis Style with custom link colour
-\graphicspath{{../figures/}}            % Location of your graphics files
-\usepackage[round]{natbib}              % Use Natbib style for the refs.
-\usepackage{bibentry}                   % Use bibentry for prepublished works
-\nobibliography*                        % Use bibentry for prepublished works
-\usepackage{attrib}                     % Use the attrib package for quotations
-\hypersetup{colorlinks=true}            % Set to false for black/white printing
-\hypersetup{pdfstartpage=1}             % Set first page to skip copyright declaration
-
-\usepackage{blindtext}                  % TODO: removeme
-
+\documentclass[sotoncolour]{uosarticle}
+\graphicspath{{../figures/}}
+\usepackage[round]{natbib}
+\hypersetup{colorlinks=true}
 %% ----------------------------------------------------------------
@@
 %\GROUP       {\MakeUppercase{\groupname}}
-\title       {BSc Project Report}
+\title       {BSc Pre-Project Review}
 \modulename  {PH4111}
@@
 %% ------------------ FRONT MATTER ORGANISATION -------------------
-\pagenumbering{gobble} % removes page number
-\raggedright           % Set the style to left justification, remove for fill justification
-
 \frontmatter
@@
 \begin{abstract}
-\input{00-abstract}
+This work is about \dots
 \end{abstract}
-\pdfbookmark[0]{\contentsname}{toc} % Add pdf bookmark for contents page for navigation
-\tableofcontents
-\listoffigures
-\listoftables
-\addtotoc{Listings} % The list of listings does not, by default, appear in the ToC
-\lstlistoflistings
-\listofaddmaterial
 \mainmatter
 %% ------------------ MAIN MATTER (CONTENT) --------------------
-\input{10-introduction}
-\input{30-experiment}
-\input{50-results}
-\input{70-conclusions}
+\section{Introduction} \label{sec:Introduction}
+Insert introduction here.
 
+\section{Conclusions} \label{sec:Conclusions}
+Draw conclusions here.
+\acknowledgements{Thanks to ...}
+\backmatter
 \appendix
-\input{90-appendix-a}
-\backmatter
 \bibliographystyle{plainnat}
-\bibliography{references}
-\chapter{Bibliography}
-To use bibliography as well as the references section use the \texttt{multibbl} package.
+\bibliography{UOS}
+%% ----------------------------------------------------------------
+\section{Stuff} \label{Section:Stuff}
+Insert stuff here.
 \end{document}

### 2021-10-28 article/article.tex
Fix references in article
Update article with example text

@@
 \hypersetup{colorlinks=true}
-%% ----------------------------------------------------------------
-%% --------------------THESIS/DOC INFORMATION ---------------------
-%\faculty     {Faculty of Science}
-%\FACULTY     {\MakeUppercase{\facname}}
+
+\usepackage{blindtext} % todo: removeme
+
 \department  {School of Physics and Astronomy}
-\DEPARTMENT  {\MakeUppercase{\deptname}}
-%\group       {[Group name]}
-%\GROUP       {\MakeUppercase{\groupname}}
-\title       {BSc Pre-Project Review}
+\title       {Pre-Project Review}
 \modulename  {PH4111}
@@
 \begin{document}
-%% ------------------ FRONT MATTER ORGANISATION -------------------
 \frontmatter
@@
 \end{abstract}
+
 \mainmatter
-%% ------------------ MAIN MATTER (CONTENT) --------------------
+
 \section{Introduction} \label{sec:Introduction}
-Insert introduction here.
+\blindtext[2]
+		\[{\frac{d}{dx}} \int _{a}^{b} f(x,t)\,dt = f{\big (}x, b{\big )} \cdot {\frac {db}{dx}} - f{\big (}x, a{\big )} \cdot {\frac{da}{dx}} + \int _{a}^{b}{\frac{\partial}{\partial x}} f(x,t)\,dt\]
+		assuming \(-\infty < a(x)\) and \(b(x) < \infty\).
+\blindtext[1]
+\begin{equation}\label{eqn:test}
+		\int_{-\infty}^{\infty} f(x)\,dx = \int_{-\infty}^{\infty} f(|\alpha| x - \sum_{i}\frac{\gamma_i}{x - \beta_i})\,dx
+\end{equation}
+	Equation \ref{eqn:test} holds for arbitrary \(\alpha\), \(\gamma_i\), \(\beta_i\).
+\blindtext[1]
+\begin{equation}
+	\int_{0}^{\infty} x^b e^{-a x} dx = \frac{\Gamma(b+1)}{a^{b+1}}
+\end{equation}
+\begin{equation}
+	\int_{0}^{\infty} \frac{x^t}{e^x - 1} \frac{dx}{x} = \zeta(t) \gamma(t)
+\end{equation}
+\blindtext[1]
 
@@
 Draw conclusions here.
+\blindtext[4]
+\begin{table}
+\begin{tabular}{c|c|c|c|c|c|c|c}
+    {$m$} & {$\Re\{\underline{\mathfrak{X}}(m)\}$} & {$-\Im\{\underline{\mathfrak{X}}(m)\}$} & {$\mathfrak{X}(m)$} & {$\frac{\mathfrak{X}(m)}{23}$} & {$A_m$} & {$\varphi(m)\ /\ ^{\circ}$} & {$\varphi_m\ /\ ^{\circ}$} \\ \toprule
+    1  & 16.128 & +8.872 & 16.128 & 1.402 & 1.373 & -146.6 & -137.6 \\
+    2  & 3.442  & -2.509 & 3.442  & 0.299 & 0.343 & 133.2  & 152.4  \\
+    3  & 1.826  & -0.363 & 1.826  & 0.159 & 0.119 & 168.5  & -161.1 \\
+    4  & 0.993  & -0.429 & 0.993  & 0.086 & 0.08  & 25.6   & 90     \\
+    5  & 1.29   & +0.099 & 1.29   & 0.112 & 0.097 & -175.6 & -114.7 \\
+    6  & 0.483  & -0.183 & 0.483  & 0.042 & 0.063 & 22.3   & 122.5  \\
+    7  & 0.766  & -0.475 & 0.766  & 0.067 & 0.039 & 141.6  & -122   \\
+    8  & 0.624  & +0.365 & 0.624  & 0.054 & 0.04  & -35.7  & 90     \\
+    9  & 0.641  & -0.466 & 0.641  & 0.056 & 0.045 & 133.3  & -106.3 \\
+    10 & 0.45   & +0.421 & 0.45   & 0.039 & 0.034 & -69.4  & 110.9  \\
+    11 & 0.598  & -0.597 & 0.598  & 0.052 & 0.025 & 92.3   & -109.3 \\
+\end{tabular}
+\caption{\label{tbl:test}Insert table caption here.}
+\end{table}
+
+\blindtext[3]
+
 \acknowledgements{Thanks to ...}
+
 \backmatter
@@
 \bibliographystyle{plainnat}
-\bibliography{UOS}
+\bibliography{references}
 %% ----------------------------------------------------------------

### 2021-11-19 article/article.tex
Change bibliography style

--- 2021-09-05 article/article.tex
@@
 \graphicspath{{../figures/}}
-\usepackage[round]{natbib}
 \hypersetup{colorlinks=true}
-%% ----------------------------------------------------------------
-%% --------------------THESIS/DOC INFORMATION ---------------------
-%\faculty     {Faculty of Science}
-%\FACULTY     {\MakeUppercase{\facname}}
+
+\usepackage[
+    backend=biber,
+    style=phys,
+    natbib=true,
+    url=false, 
+    doi=false,
+    eprint=false,
+    autocite=superscript
+]{biblatex}
+\addbibresource{references.bib}
+
 \department  {School of Physics and Astronomy}
-\DEPARTMENT  {\MakeUppercase{\deptname}}
-%\group       {[Group name]}
-%\GROUP       {\MakeUppercase{\groupname}}
-\title       {BSc Pre-Project Review}
+\title       {Pre-Project Review}
 \modulename  {PH4111}
@@
 \end{abstract}
+
 \mainmatter
-%% ------------------ MAIN MATTER (CONTENT) --------------------
+
 \section{Introduction} \label{sec:Introduction}
-Insert introduction here.
+Why millimetre waves?
+Mention the meteorological radar range equation.
+Brief mention of Rayleigh scattering.
+The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
+\begin{equation}
+	y = m x + c\label{eqn:MeteoRange}
+\end{equation}
+
+\section{Pulse Doppler radar} \label{sec:PulseDopperRadar}
+
+\section{Continuous wave radar} \label{sec:CWR}
+
+\section{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
 
 \section{Conclusions} \label{sec:Conclusions}
-Draw conclusions here.
-\acknowledgements{Thanks to ...}
+
 \backmatter
-\appendix
-\bibliographystyle{plainnat}
-\bibliography{UOS}
-%% ----------------------------------------------------------------
-\section{Stuff} \label{Section:Stuff}
-Insert stuff here.
+\printbibliography
 \end{document}
-%% ----------------------------------------------------------------

### 2021-11-19 article/article.tex
Rough structure

@@
 Why millimetre waves?
-Mention the meteorological radar range equation.
+Why is meteorological radar useful?
+
+\section{Meteorological radar}
+\subsection{Radar range equation}
+Mention the radar range equation.
 Brief mention of Rayleigh scattering.
@@
 
-\section{Pulse Doppler radar} \label{sec:PulseDopperRadar}
+\section{Types of radar}
+\subsection{Pulse Doppler radar} \label{sec:PulseDopperRadar}
+Brief introduction to pulse Doppler radar.
 
-\section{Continuous wave radar} \label{sec:CWR}
+\subsection{Continuous wave radar} \label{sec:CWR}
+Introduction to continuous wave radar.
 
-\section{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
+\subsection{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
+Continuous wave radar is useless without frequency modulation etc etc.
+Why is this better than pulse Doppler radar?
+
+\subsection{Solid state 94-GHz FMCW cloud profiling radar}
+Discuss the radar at St. Andrews.
+
+\subsubsection{Project work}
+Discuss the rationale behind this project.
 

### 2021-11-19 article/article.tex
Change article style

@@
-\documentclass[sotoncolour]{uosarticle}
+\documentclass{article}
+
+\usepackage[a4paper, margin=1in]{geometry}
+\usepackage[onehalfspacing]{setspace} % Correct 1.5 line spacing
+
+\usepackage{graphicx}  % Figures
 \graphicspath{{../figures/}}
-\hypersetup{colorlinks=true}
 
-\usepackage[
-    backend=biber,
-    style=phys,
-    natbib=true,
-    url=false, 
-    doi=false,
-    eprint=false,
-    autocite=superscript
-]{biblatex}
+\usepackage{fontspec}  % Fonts
+\usepackage{helvet}
+\usepackage{newpxtext,newpxmath}
+\defaultfontfeatures{Scale=MatchLowercase, Ligatures=TeX}
+
+\usepackage{url}
+\usepackage{hyperref}  % Links
+\usepackage{titlesec}  % Modify title/section/chapter commands
+\usepackage{mathtools} % 
+\usepackage{gensymb}   % \degree symbol
+
+\usepackage{booktabs}  % \toprule, etc., in tables
+
+\usepackage{caption}   % Caption figures
+\DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
+\DeclareCaptionFont{captiontextfont}{\sffamily}
+\captionsetup{labelfont=captionlabelfont, textfont=captiontextfont}
+
+\usepackage{fancyhdr}  % Fancy header/footer
+\pagestyle{fancy}
+\fancyhf{}
+\fancyfoot[C]{\thepage}
+%\renewcommand{\headrulewidth}{0pt}
+
+\renewcommand{\thefootnote}{\fnsymbol{footnote}} % Change footnote style
+
+% Bibliography
+\usepackage[backend=biber, style=phys, natbib=true,
+			url=false, doi=false, eprint=false,
+			autocite=superscript]{biblatex}
 \addbibresource{references.bib}
 
-\department  {School of Physics and Astronomy}
+%\department  {School of Physics and Astronomy}
 \title       {Pre-Project Review}
-\modulename  {PH4111}
-\authors     {180014855}
-\date        {\today}
+%\modulename  {PH4111}
+%\authors     {180014855}
+%\date        {\today}
 
 \begin{document}
-\frontmatter
-\maketitle
+
+\begin{titlepage}
+	\centering
+	{\includegraphics[width=0.3\textwidth]{uos-logo}}
+	\par\vspace{1cm}
+	{\LARGE University of St. Andrews\par}
+	\vspace{1cm}
+	{\Large Final year project\par}
+	\vspace{1.5cm}
+	{\huge\bfseries Millimetre-wave cloud profiling radar\par}
+	{\huge\bfseries Pre-Project Review\par}
+	\vspace{2cm}
+	{\Large 180014855\par}
+	{\small Word count: 2000\par}
+	{\small Module: PH4111}
+	\vfill
+
+	{\large \today\par}
+\end{titlepage}
+
 \begin{abstract}
@@
 
-\mainmatter
+%\mainmatter
 
@@
 
-\backmatter
+%\backmatter
 \printbibliography

### 2021-11-19 article/article.tex
Finalise new style
Fix header style
Draft, v2

--- 2021-11-19 article/article.tex
@@
-\documentclass[sotoncolour]{uosarticle}
+\documentclass{article}
+
+\usepackage[a4paper, margin=1in]{geometry}
+\usepackage[onehalfspacing]{setspace} % Correct 1.5 line spacing
+
+\usepackage{graphicx}  % Figures
 \graphicspath{{../figures/}}
-\hypersetup{colorlinks=true}
 
-\usepackage[
-    backend=biber,
-    style=phys,
-    natbib=true,
-    url=false, 
-    doi=false,
-    eprint=false,
-    autocite=superscript
-]{biblatex}
+\usepackage{fontspec}  % Fonts
+\usepackage{helvet}
+\usepackage{newpxtext,newpxmath}
+\defaultfontfeatures{Scale=MatchLowercase, Ligatures=TeX}
+
+\usepackage{url}
+\usepackage[pdfusetitle]{hyperref}
+\usepackage{titlesec}      % Modify title/section/chapter commands
+\usepackage{mathtools}     % Various maths related commands
+\usepackage{gensymb}       % \degree symbol
+\usepackage[thinc]{esdiff} % Derivatives
+\usepackage{booktabs}      % \toprule, etc., in tables
+
+% https://tex.stackexchange.com/a/43009
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+% Caption figures
+\usepackage{caption}
+\DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
+\DeclareCaptionFont{captiontextfont}{\sffamily}
+\captionsetup{labelfont=captionlabelfont, textfont=captiontextfont}
+
+% Change footnote style
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% Fancy header/footer
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\renewcommand{\sectionmark}[1]{\markright{\thesection . #1}}
+\fancyhf{}
+\lhead{\fancyplain{}{\thepage}}
+\rhead{\fancyplain{}{\textit{\rightmark}}}
+
+% Bibliography
+\usepackage[backend=biber, style=phys, natbib=true,
+			url=false, isbn=false, doi=false, eprint=false,
+			autocite=superscript]{biblatex}
+
 \addbibresource{references.bib}
 
-\department  {School of Physics and Astronomy}
-\title       {Pre-Project Review}
-\modulename  {PH4111}
-\authors     {180014855}
-\date        {\today}
+\newcommand\mytitle    {Millimetre-Wave Cloud Profiling Radar}
+\newcommand\mysubtitle {Pre-Project Review}
+\newcommand\myauthor   {180014855}
+\newcommand\mydate     {\today}
+\newcommand\mymodule   {PH4111}
+\newcommand\mywordcount{2000}
+
+\title {\mytitle}
+\author{\myauthor}
+\date  {\mydate}
 
 \begin{document}
-\frontmatter
-\maketitle
+
+\begin{titlepage}
+	\centering
+	{\includegraphics[width=0.3\textwidth]{uos-logo}}
+	\par
+	{\LARGE\bfseries University of St. Andrews\par}
+	{\LARGE School of Physics and Astronomy\par}
+	\vspace{1.5cm}
+	{\huge\bfseries\mytitle\par}
+	{\Large\mysubtitle\par}
+	\vspace{2cm}
+	{\Large\myauthor\par}
+	{\large\textbf{Module:} \mymodule\par}
+	{\large\textbf{Word count:} \mywordcount\par}
+	\vfill
+	{\large\today\par}
+\end{titlepage}
+
 \begin{abstract}
@@
 
-\mainmatter
+\section{Introduction}
+Meteorological radar systems provide great insight into weather phenomona, allowing for improved forecasts and for meteorologists to study clouds on a large scale.
+Clouds have a great influence on Earth's surface temperature, being able to both reflect and trap solar radiation, thus it is essential to study clouds to predict climate change.
+However, the high cost of conventional pulse Doppler radars limits deployment and hence the amount of cloud profling data that can be gathered.
 
-\section{Introduction} \label{sec:Introduction}
-Why millimetre waves?
-Mention the meteorological radar range equation.
-Brief mention of Rayleigh scattering.
-The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
+Millimetre waves, particularly at 35 GHz and 94 GHz, are ideally suited to cloud radars due to their atmospheric attenuation properties \dots
+Conventional pulse Doppler radars are expensive and require high peak power in contrast to frequency-modulated continuous wave (FMCW) radars, which require an average power potentially \dots less.
+High carrier frequencies of FMCW radars allow for improved range and velocity resolution \dots
+
+\section{Meteorological radar}
+\subsection{Radar range equation}
+The meteorological radar range equation relates the received and transmitted powers by 
 \begin{equation}
-	y = m x + c\label{eqn:MeteoRange}
+	P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \cdot \frac{\pi r^2 \theta \phi c \tau}{8} \cdot \frac{1}{2\ln{2}} \cdot \sum_{i=1}^N{\sigma_i} = \frac{P_t G_t G_r \lambda^2 \theta \phi c \tau}{1024 (\ln{2}) \pi^2 r^2} \sum_{i=1}^N{\sigma_i}, \label{eqn:MeteoRange}
+\end{equation}
+where \(P_r\) and \(P_t\) are the received and transmitted powers, \(G_r\) and \(G_t\) are receiver and transmitter attenna gains, \(\lambda\) is the carrier wavelength, \(r\) is the target range, \(\theta\) and \(\phi\) are the angular widths of the main lobe, \(\tau = 1/2B\), and \(\sigma_i\) is the radar cross-section (RCS) of target \(i\).
+The first term is simply the radar range equation for a point target.
+The second term is the volume sampled by the radar.
+The third term is a correction derived by Probert-Jones in 1962, arising from the non-uniform gain profile.\supercite{ProbertJones} The last term accounts for the number of particles and their individual radar cross-sections.
+
+In the Rayleigh scattering regime, the RCS takes the form
+\begin{align}
+	\sigma_i = \frac{\pi^5}{\lambda^4} D_i^6 \abs{K}^2 &&
+	\abs{K}^2 \approx \begin{cases}
+		0.93  & \text{water phase}, \\
+		0.197 & \text{ice phase},   \\
+	\end{cases}\label{eqn:RCS}
+\end{align}
+where \(D_i\) is the \(i\)th drop diameter.\supercite{RadarHandbookMeteoRange}
+
+\subsection{Frequency-modulated continuous wave radar}
+\begin{figure}
+	\includegraphics[width=\textwidth]{chirp}
+	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform.}
+	\label{fig:Chirp}
+\end{figure}
+
+Frequency-modulated continuous wave (FMCW) radar systems emit consecutive 'chirps' - signals whose frequency is a function of time, often a triangle or sawtooth wave.
+The reflected chirp arrives at a time \(\Delta t\) after emission, leading to a phase difference as shown in Figure \ref{fig:Chirp}.
+The transmitted and received signals are passed through a mixer to extract their difference/intermediate frequency (IF).
+
+\paragraph{Range measurement.} The target range relates to the time delay and hence the intermediate frequency by
+\begin{equation}
+	r = \frac{c \Delta t}{2} = \frac{c f_{IF}}{2} \diff{f}{t}.
+\end{equation}
+In practice, there are many received signals, thus one performs a discrete Fourier transform of the IF signal to obtain a range profile.
+The range resolution is limited only by the bandwidth \(B\) of the chirp:
+\begin{equation}
+	d_{res} = \frac{c}{2B}.
 \end{equation}
 
-\section{Pulse Doppler radar} \label{sec:PulseDopperRadar}
+\paragraph{Velocity measurement.} Velocity data is obtained by analysing the phase of the IF signal \dots
 
-\section{Continuous wave radar} \label{sec:CWR}
+\subsection{Solid state 94-GHz FMCW cloud profiling radar}
+The Millimetre Wave and EPR Group at the University of St Andrews has been developing a ground-based, zenith-pointing radar that operates at 94 GHz.
+\supercite{StAndrewsRadar} The radar utilises solid-state electronics and two Fresnel zone plate antennas, significantly reducing the cost.
 
-\section{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
+\subsubsection{Project work}
+The radar software needs to be updated to allow for continuous data output to netCDF files, a format widely used by meteorologists.
+This data can be processed to obtain reflectivity as a function of height, Doppler velocity moments (mean, skew, kurtosis), among other quantities used by meteorologists.
 
-\section{Conclusions} \label{sec:Conclusions}
+\subsection{Radar output}
+Reflectivity, Doppler velocity (mean, width, skew, kurtosis)
+Why are these useful for meteorologists?
 
-\backmatter
+\section{Conclusions}
+
 \printbibliography

### 2022-01-08 article/article.tex
Draft, v3

--- 2021-11-19 article/article.tex
@@
 \usepackage{url}
-\usepackage{hyperref}  % Links
+\usepackage[pdfusetitle]{hyperref}
 \usepackage{titlesec}      % Modify title/section/chapter commands
-\usepackage{mathtools} % 
+\usepackage{mathtools}     % Various maths related commands
 \usepackage{gensymb}       % \degree symbol
-
+\usepackage[thinc]{esdiff} % Derivatives
 \usepackage{booktabs}      % \toprule, etc., in tables
 
-\usepackage{caption}   % Caption figures
+% SI units
+\usepackage{siunitx}   
+\sisetup{separate-uncertainty=true,number-mode=text,detect-weight=true}
+\DeclareSIUnit\belm{Bm}
+\DeclareSIUnit\belw{BW}
+\DeclareSIUnit\beli{Bi}
+\DeclareSIUnit\belz{BZ}
+
+% https://tex.stackexchange.com/a/43009
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+% Caption figures
+\usepackage{caption}
 \DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
@@
 
-\usepackage{fancyhdr}  % Fancy header/footer
+% Change footnote style
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% Fancy header/footer
+\usepackage{fancyhdr}
 \pagestyle{fancy}
+\renewcommand{\sectionmark}[1]{\markright{\thesection . #1}}
 \fancyhf{}
-\fancyfoot[C]{\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} % Change footnote style
+\lhead{\fancyplain{}{\thepage}}
+\rhead{\fancyplain{}{\textit{\rightmark}}}
 
@@
 \usepackage[backend=biber, style=phys, natbib=true,
-			url=false, doi=false, eprint=false,
-			autocite=superscript]{biblatex}
+			url=false, isbn=false, doi=false, eprint=false,
+			autocite=superscript, urldate=long, maxcitenames=2]{biblatex}
+
 \addbibresource{references.bib}
 
-%\department  {School of Physics and Astronomy}
-\title       {Pre-Project Review}
-%\modulename  {PH4111}
-%\authors     {180014855}
-%\date        {\today}
+\newcommand\mytitle    {Millimetre-Wave Cloud Profiling Radar}
+\newcommand\mysubtitle {Pre-Project Review}
+\newcommand\myauthor   {180014855}
+\newcommand\mydate     {\today}
+\newcommand\mymodule   {PH4111}
+\newcommand\mywordcount{1702}
+
+\title {\mytitle}
+\author{\myauthor}
+\date  {\mydate}
 
@@
 	{\includegraphics[width=0.3\textwidth]{uos-logo}}
-	\par\vspace{1cm}
-	{\LARGE University of St. Andrews\par}
-	\vspace{1cm}
-	{\Large Final year project\par}
+	\par
+	{\LARGE\bfseries University of St. Andrews\par}
+	{\LARGE School of Physics and Astronomy\par}
 	\vspace{1.5cm}
-	{\huge\bfseries Millimetre-wave cloud profiling radar\par}
-	{\huge\bfseries Pre-Project Review\par}
+	{\huge\bfseries\mytitle\par}
+	{\Large\mysubtitle\par}
 	\vspace{2cm}
-	{\Large 180014855\par}
-	{\small Word count: 2000\par}
-	{\small Module: PH4111}
+	{\Large\myauthor\par}
+	{\large\textbf{Module:} \mymodule\par}
+	{\large\textbf{Word count:} \mywordcount\par}
 	\vfill
-
-	{\large \today\par}
+	{\large\today\par}
 \end{titlepage}
 
-\begin{abstract}
-This work is about \dots
-\end{abstract}
+\section{Introduction}
+Meteorological radar systems provide great insight into weather phenomena, allowing for improved forecasts and for meteorologists to study clouds on a large scale.
+Clouds have a great influence on Earth's surface temperature, being able to both reflect and trap solar radiation, thus it is essential to study clouds to predict climate change.
+However, the high cost of conventional pulse Doppler radars limits deployment and hence the amount of cloud profiling data that can be gathered.
+One of the most significant factors is due to the high peak power requirement since, for the most of the time, the radar is not transmitting.
+Much attention has been devoted to frequency-modulated continuous wave (FMCW) radars, which, as they continuously transmit, do not require as much peak power and hence cheaper amplifiers can be used.
 
-%\mainmatter
+Cloud particles are typically much smaller than millimetre waves, thus the Rayleigh backscattering approximation may be applied to greatly simplify calculations.
+The other key advantage is the high radar cross-section (RCS), a quantity indicating how much energy is reflected by a target.
+Figure \ref{fig:RayleighCurve} illustrates that, as one increases particle size and incident frequency, the RCS increases.
+However, at wavelengths comparable to particle size, this relationship is nonlinear and better described by Mie scattering.
 
-\section{Introduction} \label{sec:Introduction}
-Why millimetre waves?
-Why is meteorological radar useful?
+In addition, millimetre waves are strongly attenuated by molecules in the atmosphere, limiting their maximum useful range to a few tens of kilometres.
+Frequencies around \SI{35}{\giga\hertz} and \SI{94}{\giga\hertz} are often used in cloud radars, since the atmospheric attenuation is at a local minimum allowing the entire range of the cloud to be probed (Fig.
+\ref{fig:Attenuation}).
+
+\begin{figure}
+	\centering
+	\begin{minipage}{0.48\textwidth}
+		\includegraphics[width=0.98\textwidth]{rayleigh-2}
+		\caption{Reflectivity of spherical particles as a function of diameter for various frequencies.\supercite{KolliasFrontier} The Rayleigh backscattering approximation is only applicable in the linear regime, where the particle size is small relative to the wavelength.
+As the ratio between particle size and wavelength increases, the behaviour is more accurately described by Mie theory.\supercite{POMRRayleighScattering}}
+		\label{fig:RayleighCurve}
+	\end{minipage}
+	\hfill
+	\begin{minipage}{0.48\textwidth}
+		\includegraphics[width=0.98\textwidth]{attenuation}
+		\caption{Atmospheric attenuation as a function of radar frequency for dry and standard atmosphere conditions.\supercite{ITURAttenuation} Peaks corresponding to absorption by molecules in the atmosphere are visible throughout.}
+		\label{fig:Attenuation}
+	\end{minipage}
+\end{figure}
 
 \section{Meteorological radar}
+
 \subsection{Radar range equation}
-Mention the radar range equation.
-Brief mention of Rayleigh scattering.
-The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
+The most important equation in radar is the \textit{range equation}, which, in its simplest form, links the power received to the power transmitted by a prefactor containing target range, wavelength, RCS, and gain.
+For a point target, the range equation takes the form
 \begin{equation}
-	y = m x + c\label{eqn:MeteoRange}
+	P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \sigma, \label{eqn:PointTarget}
 \end{equation}
+where \(\sigma\) is the RCS, \(P_t\) and \(P_r\) are the transmitted and received power, \(G_t\) and \(G_r\) are the transmit and receive antenna gains, \(\lambda\) is the radar wavelength, and \(r\) is the distance to the target.
 
-\section{Types of radar}
-\subsection{Pulse Doppler radar} \label{sec:PulseDopperRadar}
-Brief introduction to pulse Doppler radar.
+For distributed targets such as rainfall or particles in a cloud, the radar cross-section becomes \(\sigma = V\eta\), where \(V\) is the volume sampled by the radar and \(\eta\) is the volume reflectivity.
+One can show that\supercite{RadarHandbookMeteo}
+\begin{equation}
+	V = \frac{1}{8} \pi r^2 \theta \phi c \tau,
+\end{equation}
+where \(\theta\) and \(\phi\) are the angular beamwidths, measured from the centre to the \(-\)\SI{3}{\decibel} point of the main lobe.
+\(\tau\), in the case of FMCW radar, is the reciprocal of the chirp bandwidth (?explain?).
+The volume reflectivity is essentially the sum of the radar cross-sections per unit volume for each target in the volume.
+Under the Rayleigh backscattering approximation, it takes the form\supercite{RadarMeteorology}
+\begin{equation}
+	\eta = \sum_i{\sigma_i} = \frac{\pi^5}{\lambda^4} \abs{K}^2 \sum_i{D_i^6} = \frac{\pi^5}{\lambda^4} \abs{K}^2 Z,
+\end{equation}
+where \(Z\) is the radar reflectivity factor and \(\abs{K}^2\) is a constant dependent on phase (water, ice), temperature, and frequency.
+\(Z\) is by far the most important term since, when combined with range data, it allows one to distinguish cloud types or determine the precipitation intensity.
 
-\subsection{Continuous wave radar} \label{sec:CWR}
-Introduction to continuous wave radar.
+Combining the expressions for \(V\) and \(\eta\) yields the radar range equation for meteorological targets,\supercite{RadarHandbookMeteo}
+\begin{equation}
+	P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \cdot \frac{1}{2\ln{2}} \cdot \frac{\pi r^2 \theta \phi c \tau}{8} \cdot \eta = \frac{P_t G_t G_r \lambda^2 \theta \phi c \tau}{1024 (\ln{2}) \pi^2 r^2} \eta = \frac{P_t G_t G_r \theta \phi c \tau \pi^3 \abs{K}^2}{1024 (\ln{2}) \lambda^2 r^2} Z,
+	\label{eqn:MeteoRange}
+\end{equation}
+where we have added a factor \(1/(2\ln{2})\) as suggested by Probert-Jones (1962)\supercite{ProbertJones} to account for the fact that antenna gain is not uniformly distributed across the sample volume.
 
-\subsection{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
-Continuous wave radar is useless without frequency modulation etc etc.
-Why is this better than pulse Doppler radar?
+\subsection{Frequency-modulated continuous wave radar}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{chirp-2}
+	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform (own work).}
+	\label{fig:Chirp}
+\end{figure}
 
-\subsection{Solid state 94-GHz FMCW cloud profiling radar}
-Discuss the radar at St. Andrews.
+Frequency-modulated continuous wave (FMCW) radar systems emit consecutive 'chirps' - signals whose frequency is a function of time, often a triangle or sawtooth wave.
+The reflected chirp arrives at a time \(\Delta t\) after emission, leading to a phase difference as shown in Fig.
+\ref{fig:Chirp}.
+The transmitted and received signals are passed through a mixer to extract their difference/intermediate frequency (IF) on which some signal processing can be performed to determine the range and velocity.
 
-\subsubsection{Project work}
-Discuss the rationale behind this project.
+\paragraph{Range measurement.} The target range relates to the time delay and hence the intermediate frequency by
+\begin{equation}
+	r = \frac{c \Delta t}{2} = \frac{c f_{IF} T_c}{2 B}.
+\end{equation}
+In practice, there are many received signals, thus one performs a discrete Fourier transform of the IF signal to obtain a range profile, known as a range-FFT.
+Since the range-FFT is discrete, the range resolution is limited by the bandwidth \(B\) of the chirp:
+\begin{equation}
+	r_{res} = \frac{c}{2B}.
+\end{equation}
+With typical bandwidths ranging from \SI{1}{\mega\hertz} to \SI{1}{\giga\hertz}, FMCW radar allows for a range resolution anywhere from \SI{15}{\metre} to \SI{15}{\centi\metre}.
 
-\section{Conclusions} \label{sec:Conclusions}
+\paragraph{Velocity measurement.} Two targets at roughly the same range appear in the same bin on the range-FFT.
+Fortunately, it is possible to distinguish them by considering the phase of the signal in each bin across subsequent chirps.
+If a target is moving at a velocity \(v\), the phase of the IF signal changes by an amount given by
+\begin{equation}
+	\delta = \frac{4 \pi v T_c}{\lambda},
+\end{equation}
+where \(T_c\) is the chirp repetition frequency. The velocity is unambigious only if \(-\pi \le \delta \le \pi\), thus leading to a maximum velocity of
+\begin{equation}
+	v_{max} = \frac{\lambda}{4 T_c}.
+\end{equation}
+If the velocity is outwith the interval \([-v_{max}, v_{max}]\), aliasing will occur.
 
-%\backmatter
+For multiple targets, we once again perform an FFT (Doppler-FFT) on each range bin over a sequence of chirps known as a frame. This imposes a velocity resolution given by
+\begin{equation}
+	v_{res} = \frac{\lambda}{2 T_f},
+\end{equation}
+where \(T_f\) is the time per frame.
+
+\subsection{Radar output}
+\begin{table}
+	\centering
+	\begin{tabular}{l|l}
+		Reflectivity factor (dBZ) & Types and approximate base altitudes                                                               \\
+		\midrule
+		less than \(-50\)         & Cumulus (\(0.3\) to \(1.5\) \si{\kilo\metre}), altocumulus (\(2\) to \(6\) \si{\kilo\metre}), thin cirrus (\(6\) to \(12\) \si{\kilo\metre}) \\
+		\(-40\) to \(-20\)        & Stratus (\(0\) to \(1.2\) \si{\kilo\metre}), altostratus (\(3\) to \(6\) \si{\kilo\metre}), thick cirrus (\(6\) to \(12\) \si{\kilo\metre})  \\
+		\(-20\) and above         & Precipitation                                                                                     
+	\end{tabular}
+	\caption{Reflectivity factors and associated cloud types,\supercite{GorkaReflectivity} including base altitudes.\supercite{CloudTypes}.}
+	\label{tbl:dBZInterpretation}
+\end{table}
+
+We mentioned the importance of the radar reflectivity factor \(Z\) in cloud classification and measuring the intensity of precipitation.
+[Discuss: Z]
+
+Further information can be obtained from Doppler velocity spectra.
+[Discuss: mean, width, skew, kurtosis, drop size distribution]
+
+\supercite{RadarMeteorology}
+
+\subsection{Radar sensitivity}
+An important metric in characterising radar systems is the \textit{sensitivity}, often defined as the minimum detectable reflectivity. 
+\begin{equation}
+	dBZ = C + P_r + 20\log{r}
+\end{equation}
+[Add units and explain this equation, plus how to get sensitivity plot.]
+[\(P_r = SNR * noise power = SNR * bandwidth * kT\)...]
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{sensitivity}
+	\caption{Predicted minimum detectable reflectivity curve using parameters for the St.
+Andrews radar given in Table \ref{tbl:RadarSystems}.
+Assumes a signal-to-noise ratio of \(1\), a temperature of \SI{290}{\kelvin}, and \(\abs{K}^2 = 0.846\)\supercite{ComplexIndexOfRefraction} since the radar operates at \SI{94}{\giga\hertz}.
+\textit{To-do: temperature dependence of \(\abs{K}^2\), averaging, other radar systems, mark dBZ range of interest for clouds.} (own work)}
+	\label{fig:Sensitivity}
+\end{figure}
+
+\subsection{Radar systems}
+[Would like to discuss ARM here as well]
+
+\begin{table}
+	\begin{tabular}{lr|l|l|l}     & & St. Andrews\supercite{StAndrewsRadar} & BASTA\supercite{BASTA} & Huggard\supercite{HuggardRadar} \\
+		\midrule
+		\textbf{Frequency}        & (\si{\giga\hertz})    & \(94\)   & \(95\) & \\
+		\textbf{Chirp frequency}  & (\si{\hertz})         & \(6510\) & \(\) & \\
+		\textbf{Bandwidth}        & (\si{\mega\hertz})    & \(15\)   & \(\) & \\
+		\textbf{Range resolution} & (\si{\metre})         & \(10\)   & \(25\) & \\
+
+		\textbf{Transmit power}   & (\si{\deci\belm})     & \(25\)   & \(27\)--\(30\) & \\
+		\textbf{Antenna gain}     & (\si{\deci\beli})     & \(52\)   & \(54\) & \\
+		\textbf{Beamwidth}        & (\degree)             & \(0.43\) & \(0.4\) & \\
+
+		\textbf{Noise figure}     & (\si{\deci\bel})      & \(5.3\)  & \(8\) &  \\
+
+		\textbf{Weather constant} & (\si{\deci\belm})     & \(\)     & & \\
+	\end{tabular}
+	\caption{Parameters for various radar systems.}
+	\label{tbl:RadarSystems}
+\end{table}
+
+\subsubsection{Solid state \SI{94}{\giga\hertz} FMCW cloud profiling radar}
+The Millimetre Wave and EPR Group at the University of St Andrews has been developing a ground-based, zenith-pointing radar that operates at \SI{94}{\giga\hertz}.\supercite{StAndrewsRadar} The radar utilises solid-state electronics and two Fresnel zone plate antennas, significantly reducing the cost.
+
+Since FMCW radar requires thousands of FFTs to be performed, the radar software is written in C and leverages both the CPU and GPU for maximum performance.
+Since each FFT can be performed independently, multithreading can be used to further improve throughput, through this comes at the cost of increased software complexity.\supercite{Cassidy}
+Other approaches considered include specialised hardware dedicated to signal processing such as a digital signal processor (DSP) or field-programmable gate array (FPGA), though these are considerably less flexible than a conventional CPU-based design.
+
+\subsubsection{Bistatic Radar System for Atmospheric Studies (BASTA) \SI{95}{\giga\hertz} FMCW cloud radar}
+[BASTA uses FPGAs. Bandwidth and some other parameters are variable, like with the St. Andrews radar. Table \ref{tbl:RadarSystems} is a bit misleading.]
+
+\section{Project work}
+The St.
+Andrews radar software needs to be updated to allow for averaging, extraction of Doppler moments, and real-time output.
+Also, calibration and some outdoor testing needs to be performed, in particular assessing the effect of ambient temperature on radar performance.
+\paragraph{Signal averaging.} Averaging of range profiles reduces noise and increases sensitivity to low reflectivity clouds such as thin cirrus.
+Figure \ref{fig:Sensitivity} shows that without averaging the radar will be unable to detect any clouds above \SI{2}{\kilo\metre}.
+\paragraph{Doppler moments.} Extraction of Doppler moments (mean, skew, kurtosis) provides meteorologists with more information and allows them to better study the onset of cloud formation, for example.
+\paragraph{Real-time output.} Real-time saving in netCDF,\supercite{NetCDFFormat} a format widely used by meteorologists. This would allow for offline data processing.
+\paragraph{Effect of ambient temperature.} Changes in ambient temperature could affect the radar performance.
+Solid-state devices are particularly vulnerable to thermal drift.
+Thermal sensors in the radar enclosure will record the ambient temperature over a long period of time (?a day, a week, two weeks?) which can be correlated to radar performance (explain).
+\paragraph{Cross-check results with disdrometer.} Time permitting, a disdrometer located next to the radar could be used to collect reflectivity data which can then be compared to theoretical predictions and the output from the radar, providing a way to cross-check results.
+
+\section{Conclusions}
+[What was covered in this article?]
+[Future of FMCW cloud radar, problems]
+
+[Perhaps this article is a bit heavy on theory... need to better reference in theory section, particularly the range/velocity paragraphs.]
+[Some paragraphs don't flow together very well, such as introduction -> meteorological radar.]
+[Introduction is also quite light on references, doesn't really mention the scope of the article.]
+
+\nocite{*}
 \printbibliography

### 2022-01-08 notes/notes.tex
Draft, v3

--- 2021-11-19 article/article.tex
@@
 \usepackage{url}
-\usepackage{hyperref}  % Links
+\usepackage[pdfusetitle]{hyperref}
 \usepackage{titlesec}      % Modify title/section/chapter commands
-\usepackage{mathtools} % 
+\usepackage{mathtools}     % Various maths related commands
 \usepackage{gensymb}       % \degree symbol
-
+\usepackage[thinc]{esdiff} % Derivatives
 \usepackage{booktabs}      % \toprule, etc., in tables
 
-\usepackage{caption}   % Caption figures
+% https://tex.stackexchange.com/a/43009
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+% Caption figures
+\usepackage{caption}
 \DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
@@
 \usepackage[backend=biber, style=phys, natbib=true,
-			url=false, doi=false, eprint=false,
+			url=false, isbn=false, doi=false, eprint=false,
 			autocite=superscript]{biblatex}
+
 \addbibresource{references.bib}
 
-%\department  {School of Physics and Astronomy}
-\title       {Pre-Project Review}
-%\modulename  {PH4111}
-%\authors     {180014855}
-%\date        {\today}
+\newcommand\mytitle {Notes on FMCW and Meteorological Radar}
+\newcommand\myauthor{Stuart Ballantyne}
+\newcommand\mydate  {\today}
+
+\title {\mytitle}
+\author{\myauthor}
+\date  {\mydate}
 
 \begin{document}
+	\maketitle
+	\tableofcontents
+	\newpage
 
-\begin{titlepage}
+	\begin{figure}
 		\centering
-	{\includegraphics[width=0.3\textwidth]{uos-logo}}
-	\par\vspace{1cm}
-	{\LARGE University of St. Andrews\par}
-	\vspace{1cm}
-	{\Large Final year project\par}
-	\vspace{1.5cm}
-	{\huge\bfseries Millimetre-wave cloud profiling radar\par}
-	{\huge\bfseries Pre-Project Review\par}
-	\vspace{2cm}
-	{\Large 180014855\par}
-	{\small Word count: 2000\par}
-	{\small Module: PH4111}
-	\vfill
+		\includegraphics[width=0.8\textwidth]{example-output}
+		\caption{Example cloud radar output.\supercite{ExampleOutput}}
+		\label{fig:ExampleOutput}
+	\end{figure}
 
-	{\large \today\par}
-\end{titlepage}
+	\section{Radar range equation}
 
-\begin{abstract}
-This work is about \dots
-\end{abstract}
+	\subsection{Point target}
+	Consider an isotropically emitting antenna with transmit power \(P_t\).
+	The power density \(Q\) at a distance \(r\) from the antenna is given by
+	\begin{equation*}
+		Q = \frac{P_t}{4 \pi r^2}.
+	\end{equation*}
+	To account for the directivity and efficiency of the antenna one must include the (transmit) gain \(G_t\). Hence,
+	\begin{equation*}
+		Q = \frac{G_t P_t}{4 \pi r^2}.
+	\end{equation*}
+	The power reflected by a target with \textit{radar cross-section} \(\sigma\) (units of cross-sectional area) is then
+	\begin{equation*}
+		P_{refl} = Q \sigma = \frac{G_t P_t \sigma}{4\pi r^2}.
+	\end{equation*}
+	Assuming the power is reflected isotropically, then
+	\begin{equation*}
+		Q_r = \frac{P_{refl}}{4\pi r^2} = \frac{G_t P_t \sigma}{(4\pi r^2)^2}.
+	\end{equation*}
+	The receiver antenna has an effective area \(A\) given by
+	\begin{equation*}
+		A = \frac{G_r \lambda^2}{4\pi},
+	\end{equation*}
+	where \(G_r\) is the receiver antenna gain. The received power is simply the product \(P_r = A Q_r\), hence we finally arrive at
+	\begin{equation}
+		P_r = \frac{P_t G_t G_r \lambda^2}{(4\pi)^3 r^4} \sigma \label{eqn:PointRange},
+	\end{equation}
+	which is known as the \textbf{radar range equation}.
 
-%\mainmatter
+	\subsection{Meteorological targets}
+	For a distributed meteorological target, one writes
+	\begin{equation}
+		\sigma = \eta V,
+	\end{equation}
+	where \(\eta\) is the volume reflectivity (cross-sectional area per unit volume) and \(V\) is the volume sampled by the radar.
 
-\section{Introduction} \label{sec:Introduction}
-Why millimetre waves?
-Why is meteorological radar useful?
+	[Derive volume term]
 
-\section{Meteorological radar}
-\subsection{Radar range equation}
-Mention the radar range equation.
-Brief mention of Rayleigh scattering.
-The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
+	In the Rayleigh scattering regime, one can write
 	\begin{equation}
-	y = m x + c\label{eqn:MeteoRange}
+		\eta = \sum_i{\sigma_i} = \frac{\pi^5}{\lambda^4} \abs{K}^2 \sum_i{D_i^6} = \frac{\pi^5}{\lambda^4} \abs{K}^2 Z
 	\end{equation}
 
-\section{Types of radar}
-\subsection{Pulse Doppler radar} \label{sec:PulseDopperRadar}
-Brief introduction to pulse Doppler radar.
+	Thus, the \textbf{meteorological radar range equation} is
+	\begin{equation}
+		P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \cdot \frac{1}{2\ln{2}} \cdot \frac{\pi r^2 \theta \phi c \tau}{8} \cdot \eta = \frac{P_t G_t G_r \lambda^2 \theta \phi c \tau}{1024 (\ln{2}) \pi^2 r^2} \eta = \frac{P_t G_t G_r \theta \phi c \tau \pi^3 \abs{K}^2}{1024 (\ln{2}) \lambda^2 r^2} Z,
+		\label{eqn:MeteoRange}
+	\end{equation}
+	where we have inserted a factor \(1/(2\ln{2})\) to account for the Gaussian antenna gain profile.\supercite{ProbertJones}
 
-\subsection{Continuous wave radar} \label{sec:CWR}
-Introduction to continuous wave radar.
+	\pagebreak
 
-\subsection{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
-Continuous wave radar is useless without frequency modulation etc etc.
-Why is this better than pulse Doppler radar?
+	\section{Frequency-modulated continuous wave}
+	\begin{figure}
+		\includegraphics[width=\textwidth]{chirp-2}
+		\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform (own work).}
+		\label{fig:Chirp}
+	\end{figure}
 
-\subsection{Solid state 94-GHz FMCW cloud profiling radar}
-Discuss the radar at St. Andrews.
+	\section{Radar reflectivity}
+	\begin{table}
+		\begin{minipage}[r]{0.3\textwidth}
+			\begin{tabular}{|l|l|}
+				\toprule
+				Wavelength (mm)        & \(3.19\) \\
+				Range res. (m)         & \(10\)   \\
+				Transmit power (dBm)   & \(25\)   \\
+				Gain (dBi)             & \(52\)   \\
+				Beamwidth (\degree)    & \(0.43\) \\
+				Chirp rep. freq. (GHz) & \(6510\) \\
+				Noise figure (dB)      & \(5.3\)  \\
+				\bottomrule
+			\end{tabular}
+		\caption{Parameters for the St. Andrews 94-GHz cloud profiling radar.\supercite{StAndrewsRadar}}
+		\end{minipage}
+	\end{table}
 
-\subsubsection{Project work}
-Discuss the rationale behind this project.
-
-\section{Conclusions} \label{sec:Conclusions}
-
-%\backmatter
+	\nocite{*} % Show all references.
 	\printbibliography

### 2022-01-22 article/article.tex
Submission

--- 2021-11-19 article/article.tex
@@
 
+\usepackage{url}
+\usepackage[pdfusetitle]{hyperref}
+\usepackage{titlesec}      % Modify title/section/chapter commands
+\usepackage{mathtools}     % Various maths related commands
+\usepackage{gensymb}       % \degree symbol
+\usepackage[thinc]{esdiff} % Derivatives
+\usepackage{booktabs}      % \toprule, etc., in tables
+\usepackage{doi}           % support DOI links in bibliography
+\usepackage{wrapfig}       % figures in text
+
 \usepackage{fontspec}  % Fonts
@@
 
-\usepackage{url}
-\usepackage{hyperref}  % Links
-\usepackage{titlesec}  % Modify title/section/chapter commands
-\usepackage{mathtools} % 
-\usepackage{gensymb}   % \degree symbol
+% SI units
+\usepackage{siunitx}
+\sisetup{separate-uncertainty=true,number-mode=text,detect-weight=true}
+\DeclareSIUnit\belm{Bm}
+\DeclareSIUnit\belw{BW}
+\DeclareSIUnit\beli{Bi}
+\DeclareSIUnit\belz{BZ}
 
-\usepackage{booktabs}  % \toprule, etc., in tables
+% https://tex.stackexchange.com/a/43009
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
 
-\usepackage{caption}   % Caption figures
+% Caption figures
+\usepackage{caption}
 \DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
@@
 
-\usepackage{fancyhdr}  % Fancy header/footer
+% Change footnote style
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% Fancy header/footer
+\usepackage{fancyhdr}
 \pagestyle{fancy}
+\renewcommand{\sectionmark}[1]{\markright{\thesection . #1}}
 \fancyhf{}
-\fancyfoot[C]{\thepage}
-%\renewcommand{\headrulewidth}{0pt}
-
-\renewcommand{\thefootnote}{\fnsymbol{footnote}} % Change footnote style
+\lhead{\fancyplain{}{\thepage}}
+\rhead{\fancyplain{}{\textit{\rightmark}}}
 
 % Bibliography
-\usepackage[backend=biber, style=phys, natbib=true,
-			url=false, doi=false, eprint=false,
-			autocite=superscript]{biblatex}
+\usepackage[backend=biber, style=ieee, natbib=true,
+			url=false, isbn=true, doi=true,
+			eprint=false, urldate=long]{biblatex}
 \addbibresource{references.bib}
 
-%\department  {School of Physics and Astronomy}
-\title       {Pre-Project Review}
-%\modulename  {PH4111}
-%\authors     {180014855}
-%\date        {\today}
+% biblatex IEEE style leaves empty parentheses when there is no date/year field.
+% Since there are no date fields for many online resources, we use
+%   https://tex.stackexchange.com/a/151264
+% to stop these parentheses from being generated if there is no date field.
+\usepackage{xpatch}
+\xpatchbibdriver{online}
+{\printtext[parens]{\usebibmacro{date}}}
+{\iffieldundef{year}
+	{}
+	{\printtext[parens]{\usebibmacro{date}}}}
+{}
+{\typeout{There was an error patching biblatex-ieee (specifically, ieee.bbx's @online driver)}}
+
+% Fix for missing µ in siunitx ???
+% https://tex.stackexchange.com/a/428215
+\sisetup{math-micro=\text{µ},text-micro=µ}
+
+\newcommand\mytitle    {Millimetre-Wave Cloud Profiling Radar}
+\newcommand\mysubtitle {Pre-Project Review}
+\newcommand\myauthor   {180014855}
+\newcommand\mydate     {\today}
+\newcommand\mymodule   {PH4111}
+\newcommand\mywordcount{2300}
+
+\title {\mytitle}
+\author{\myauthor}
+\date  {\mydate}
 
@@
 	{\includegraphics[width=0.3\textwidth]{uos-logo}}
-	\par\vspace{1cm}
-	{\LARGE University of St. Andrews\par}
-	\vspace{1cm}
-	{\Large Final year project\par}
+	\par
+	{\LARGE\bfseries University of St Andrews\par}
+	{\LARGE School of Physics and Astronomy\par}
 	\vspace{1.5cm}
-	{\huge\bfseries Millimetre-wave cloud profiling radar\par}
-	{\huge\bfseries Pre-Project Review\par}
+	{\huge\bfseries\mytitle\par}
+	{\Large\mysubtitle\par}
 	\vspace{2cm}
-	{\Large 180014855\par}
-	{\small Word count: 2000\par}
-	{\small Module: PH4111}
+	{\Large\myauthor\par}
+	{\large\textbf{Module:} \mymodule\par}
+	{\large\textbf{Word count:} \mywordcount\par}
 	\vfill
-
-	{\large \today\par}
+	{\large\today\par}
 \end{titlepage}
 
-\begin{abstract}
-This work is about \dots
-\end{abstract}
+\section{Introduction}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{example-output}
+	\caption{Example range-time plot from a cloud profiling radar.\supercite{RPG}}
+	\label{fig:ExampleOutput}
+\end{figure}
+Meteorological radar systems provide great insight into weather phenomena, allowing for improved forecasts and for meteorologists to study clouds on a large scale.
+Clouds have a great influence on Earth’s surface temperature, being able to both reflect and trap solar radiation, thus it is essential to study clouds to accurately model climate change.
+However, the high cost of conventional pulse-Doppler radars limits their deployment and hence the amount of cloud data that can be gathered.\supercite{Illingworth} Much attention has been devoted to frequency-modulated continuous wave (FMCW) radars which require significantly less power and so less expensive amplifiers can be used.
+FMCW radars generally offer better range resolution compared to pulse-Doppler systems.
 
-%\mainmatter
+Millimetre waves are particularly suitable for cloud radars due to having high reflectivity to small particles such as cloud droplets (\(0.01\) to \SI{0.1}{\milli\metre})\supercite{FirstCourse} whilst still penetrating cloud layers.
+However, at millimetre wavelengths attenuation from the atmosphere is a significant problem.\supercite{KolliasFrontier} For this reason most cloud radars operate near local minima in the absorption spectrum (Fig.
+\ref{fig:Attenuation}), usually \SI{35}{\giga\hertz} or \SI{94}{\giga\hertz}.
+Higher frequencies are preferred for cloud radars due to increased radar cross-section (RCS) for smaller particles (Fig.
+\ref{fig:RayleighCurve}).
+At wavelengths close to particle diameter, the RCS begins to taper off and becomes more accurately described by Mie scattering theory,\supercite{POMRRayleighScattering} which complicates calculations.
 
-\section{Introduction} \label{sec:Introduction}
-Why millimetre waves?
-Why is meteorological radar useful?
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{attenuation}
+	\caption{Atmospheric attenuation as a function of radar frequency for dry and standard atmosphere conditions.\supercite{ITURAttenuation} Peaks corresponding to absorption by molecules in the atmosphere are visible throughout.}
+	\label{fig:Attenuation}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{rayleigh}
+	\caption{Radar cross-section of spherical particles as a function of radius and wavelength.
+The Rayleigh backscattering approximation is only applicable in the linear regime, where the particle size is small relative to the wavelength.
+As the ratio between particle size and wavelength increases, the behaviour is more accurately described by Mie theory.\supercite{POMRRayleighScattering}}
+	\label{fig:RayleighCurve}
+\end{figure}
 
-\section{Meteorological radar}
-\subsection{Radar range equation}
-Mention the radar range equation.
-Brief mention of Rayleigh scattering.
-The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
+\section{Frequency-modulated continuous wave radar}
+FMCW radar systems emit consecutive 'chirps' - signals whose frequency is linearly modulated by triangular or more commonly sawtooth The reflected chirp arrives at a time \(\Delta t\) after emission, leading to a phase difference as shown in Fig.
+\ref{fig:Chirp}.
+The transmitted and received signals are passed through a mixer to extract their difference/intermediate frequency (IF) on which some signal processing can be performed to determine the range and velocity.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{chirp-3}
+	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform. (Own work)}
+	\label{fig:Chirp}
+\end{figure}
+
+\paragraph{Range measurement.} The target range relates to the time delay and hence the intermediate frequency \(f_{IF}\) by
 \begin{equation}
-	y = m x + c\label{eqn:MeteoRange}
+	r = \frac{c \Delta t}{2} = \frac{c f_{IF} T_c}{2 B},
+\end{equation}
+where \(r\) is the distance from the radar and \(T_c\) is the chirp duration.\supercite{TIFMCWDoppler}
+In practice, there are many received signals, thus one performs a discrete Fourier transform of the IF signal to obtain a range profile, known as a range-FFT.
+Since the range-FFT is discrete, the range resolution is limited by the bandwidth \(B\) of the chirp:
+\begin{equation}
+	r_{res} = \frac{c}{2B}.
 \end{equation}
 
-\section{Types of radar}
-\subsection{Pulse Doppler radar} \label{sec:PulseDopperRadar}
-Brief introduction to pulse Doppler radar.
+\paragraph{Velocity measurement.} Two targets at roughly the same range appear in the same bin on the range-FFT.
+Fortunately, it is possible to distinguish them by considering the phase of the signal in each bin across subsequent chirps.
+If a target is moving at a velocity \(v\), the phase of the IF signal changes by an amount given by\supercite{TIFMCWDoppler}
+\begin{equation}
+	\delta = \frac{4 \pi v T_c}{\lambda},
+\end{equation}
+where \(v\) is the target velocity. The velocity is unambigious only if \(-\pi \le \delta \le \pi\), thus leading to a maximum velocity of
+\begin{equation}
+	v_{max} = \frac{\lambda}{4 T_c}.
+\end{equation}
+If the velocity is outwith the interval \([-v_{max}, v_{max}]\), it will 'fold' back in on itself (aliasing).
 
-\subsection{Continuous wave radar} \label{sec:CWR}
-Introduction to continuous wave radar.
+For multiple targets, we once again perform an FFT (Doppler-FFT)\supercite{POMRDopplerProcessing} on each range bin over a sequence of chirps known as a frame.
+This imposes a velocity resolution given by
+\begin{equation}
+	v_{res} = \frac{\lambda}{2 T_f},
+\end{equation}
+where \(T_f\) is the time per frame.
 
-\subsection{Frequency-modulated continuous wave radar} \label{sec:FMCWR}
-Continuous wave radar is useless without frequency modulation etc etc.
-Why is this better than pulse Doppler radar?
+\section{Meteorological radar theory}
+The range equation for a point target is given by
+\begin{equation}
+	P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \sigma, \label{eqn:PointTarget}
+\end{equation}
+where \(P_t\) and \(P_r\) are the transmitter and receiver powers, \(G_t\) and \(G_r\) are transmitter and receiver antenna gains, and \(\sigma\) is the radar cross-section. For distributed targets,
+\begin{equation}
+	\sigma = V \eta,
+\end{equation}
+where \(V\) is the radar sample volume and \(\eta\) is the volume reflectivity.
 
-\subsection{Solid state 94-GHz FMCW cloud profiling radar}
-Discuss the radar at St. Andrews.
+It can be seen from Fig. \ref{fig:Volume} that
+\begin{equation}
+	V = \frac{1}{8} \pi r^2 \theta \phi \Delta R,
+\end{equation}
+where \(\theta\) and \(\phi\) are the angular beamwidths, measured from the centre to the \(-\SI{3}{\decibel}\) point of the main lobe.
+The depth of the range cell \(\Delta R = c\tau\) is given by the pulse width \(\tau\) for pulsed radars, or for FMCW radar \(\tau\) is the reciprocal of the chirp bandwidth \(B\).\supercite{Gorka}
 
-\subsubsection{Project work}
-Discuss the rationale behind this project.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{volume}
+	\caption{Diagram of radar sample volume.\supercite{Gorka}}
+	\label{fig:Volume}
+\end{figure}
 
-\section{Conclusions} \label{sec:Conclusions}
+The volume reflectivity is essentially the sum of the radar cross-sections for each target per unit volume. Under the Rayleigh backscattering approximation, it takes the form\supercite{FirstCourse}
+\begin{equation}
+	\eta = \frac{1}{V}\sum_i{\sigma_i} = \frac{\pi^5}{\lambda^4} \abs{K}^2 \frac{\sum_i{D_i^6}}{V} = \frac{\pi^5}{\lambda^4} \abs{K}^2 Z,
+\end{equation}
+where \(Z\) is the radar reflectivity factor and \(K\) is a constant dependent on phase (water, ice), temperature, and frequency.
+\(Z\) is by far the most important term since it is independent of radar parameters and can be used to determine cloud types and precipitation intensity.
+Since values for \(Z\) span many orders of magnitude, it is often expressed on a logarithmic scale \(dBZ\).
 
-%\backmatter
+Combining the expressions for \(V\) and \(\eta\) yields the range equation for meteorological targets,\supercite{RadarHandbookMeteo}
+\begin{equation}
+	P_r = \frac{P_t G_t G_r \lambda^2}{(4 \pi)^3 r^4} \cdot \frac{1}{2\ln{2}} \cdot \frac{\pi r^2 \theta \phi c \tau}{8} \cdot \eta = \frac{P_t G_t G_r \lambda^2 \theta \phi c \tau}{1024 (\ln{2}) \pi^2 r^2} \eta = \frac{P_t G_t G_r \theta \phi c \tau \pi^3 \abs{K}^2}{1024 (\ln{2}) \lambda^2 r^2} Z,
+	\label{eqn:MeteoRange}
+\end{equation}
+where we have inserted a factor of \(1/(2\ln{2})\) as suggested by Probert-Jones (1962)\supercite{ProbertJones} to account for the fact that antenna gain is not uniformly distributed across the sample volume.
+
+\subsection{Radar output}
+The radar reflectivity factor combined with the range information can be used to identify clouds and estimate precipitation intensity.
+Fig.
+\ref{fig:ExampleOutput} is a range-time plot with reflectivity on a logarithmic colour scale.
+
+Just as important is the Doppler velocity spectra and its moments (mean, width, skew, kurtosis) which provides information on microphysical processes in clouds.
+These moments are of particular interest to meteorologists who wish to study the onset of cloud formation or precipitation, for example.
+Fig. \ref{fig:ExampleDopplerSpectra} shows three Doppler spectra taken at different altitudes in a precipitating cloud, showing how the distribution changes as one moves through the melting layer.
+
+Further processing can allow one to determine particle size distribution.\supercite{DopplerMoments}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l|l}
+		Reflectivity factor (dBZ) & Types and approximate base altitudes \\
+		\midrule
+		less than \(-50\)         & Cumulus (\(0.3\) to \(1.5\) \si{\kilo\metre}), altocumulus (\(2\) to \(6\) \si{\kilo\metre}), thin cirrus (\(6\) to \(12\) \si{\kilo\metre}) \\
+		\(-40\) to \(-20\)        & Stratus (\(0\) to \(1.2\) \si{\kilo\metre}), altostratus (\(3\) to \(6\) \si{\kilo\metre}), thick cirrus (\(6\) to \(12\) \si{\kilo\metre})  \\
+		\(-20\) and above         & Precipitation
+	\end{tabular}
+	\caption{Reflectivity factors and associated cloud types,\supercite{KolliasFrontier} including base altitudes.\supercite{CloudTypes}.}
+	\label{tbl:dBZInterpretation}
+\end{table}
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.6\textwidth]{doppler-spectra}
+	\caption{Doppler velocity spectra above (top), within (middle), below (bottom) the melting layer of a precipitating cloud.\supercite{RPGPaper} Above the melting layer, the distribution is roughly Gaussian.
+Within the layer, the distribution is skewed and the mean velocity increases in magnitude, indicating the acceleration of ice particles as they melt.
+Below the layer, there is significant broadening of the velocity spectra.}
+	\label{fig:ExampleDopplerSpectra}
+\end{figure}
+
+\subsection{Radar sensitivity}
+Eqn. \ref{eqn:MeteoRange} is more useful if one writes it as a function of the signal-to-noise ratio (SNR) and the thermal noise power by substituting
+\begin{equation}
+	P_r = SNR \cdot P_n = SNR \cdot k_B T F B_r,
+	\label{eqn:SNR}
+\end{equation}
+where \(P_n\) is the thermal noise power, \(k_B\) is Boltzmann's constant, \(F\) is the noise figure (in linear units), \(T\) is the system temperature, and \(B_r\) is the receiver bandwidth.\supercite{RadarHandbookMeteo}
+Eqn.
+\ref{eqn:SNR} can be used with a minimum desired SNR to obtain the minimum detectable reflectivity (sensitivity) for a given radar.
+Most clouds have altitudes between \(0\) to \(\SI{12}{\kilo\metre}\) and a radar reflectivity factor between \(-40\) and \(-\SI{20}{\deci\belz}\)\supercite{Gorka} (Table \ref{tbl:dBZInterpretation}).
+Sensitivity curves for the radars in Table \ref{tbl:RadarSystems} are given in Fig. \ref{fig:Sensitivity}.
+
+\section{Radar systems}
+\subsection{St Andrews \SI{94}{\giga\hertz} FMCW radar}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\textwidth]{cloud-radar}
+	\caption{St Andrews cloud profiling radar.\supercite{StAndrewsRadarImage}}
+	\label{fig:RadarImage}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\textwidth]{gui}
+	\caption{Screenshot of the St Andrews cloud profiling radar user interface.\supercite{StAndrewsRadar} The peak in the frequency spectrum indicates rain.
+Aliasing is apparent in the range-Doppler plot at around \SI{1500}{\metre}, as the rain exceeds the maximum unambiguous velocity.
+Note that the radar is currently uncalibrated.}
+	\label{fig:GUI}
+\end{figure}
+
+The Millimetre Wave and EPR Group at the University of St Andrews has been developing a ground-based, zenith-pointing radar that operates at \SI{94}{\giga\hertz}.\supercite{StAndrewsRadar} The radar utilises solid-state electronics and two Fresnel zone plate antennas, significantly reducing the cost.
+Since FMCW radar requires thousands of FFTs to be performed, the radar software is written in C and leverages multiple CPU threads for best performance.
+Multithreading comes at the cost of increased software complexity.\supercite{Cassidy}
+The sensitivity at \SI{2}{\kilo\metre} is only \(-\SI{20}{\deci\belz}\), just bordering on the range of interest for clouds (\(< -\SI{20}{\deci\belz}\)).
+However, the sensitivity can be greatly improved by implementing signal averaging as shown in Fig.
+\ref{fig:Sensitivity}.
+With \SI{1}{\second} non-coherent averaging,\supercite{POMRNonCoherentAveraging} the sensitivity at \SI{2}{\kilo\metre} is improved to about \(-\SI{-38}{\deci\belz}\).
+
+\subsection{Bistatic Radar System for Atmospheric Studies (BASTA) \SI{95}{\giga\hertz} FMCW cloud radar}
+In contrast the CPU-based design of the St Andrews cloud profiling radar, the BASTA\supercite{BASTA} radar implements signal processing using field-programmable gate arrays (FPGA) for improved performance.
+However, implementing hardware-based signal processing makes it more difficult to debug and reduces the overall flexibility.\supercite{Cassidy}
+
+\subsection{Galileo \SI{94}{\giga\hertz} pulse-Doppler radar}
+The Galileo radar\supercite{Galileo} at the Chibolton Observatory is a state of the art pulse-Doppler radar that operates at \SI{94}{\giga\hertz}.
+While the radar offers better sensitivity than most radars in Table \ref{tbl:RadarSystems}, the peak power requirement (\SI{1.5}{\kilo\watt}) and the range resolution (\SI{75}{\metre}) are significantly greater.
+
+\subsection{Chiba \SI{95}{\giga\hertz} FMCW radar}
+Since 2003, Chiba University has been operating a \SI{94.7}{\giga\hertz} FMCW cloud radar\supercite{Chiba} that provides sensitivity on par with the Galileo radar.
+The antennas have narrower beamwidths (\(0.18\degree\)) than most of the other radars (\(0.4\) to \(0.5\degree\)) except Huggard (\(0.15\degree\)).
+
+\begin{table}
+	\begin{tabular}{lr|l|l|l|l|l}
+		& & St Andrews\supercite{StAndrewsRadar} & BASTA\supercite{BASTA} & Chiba\supercite{Chiba} & Huggard\supercite{HuggardRadar} & Galileo\supercite{Galileo} \\
+		\midrule
+		\textbf{Type}                    &                                            & FMCW     & FMCW     & FMCW     & FMCW     & Pulse    \\
+		\textbf{Frequency}               & (\si{\giga\hertz})                         & \(94\)   & \(95\)   & \(94.7\) & \(94\)   & \(94\)   \\
+		\textbf{Chirp/pulse rep. freq.}  & (\si{\hertz})                              & \(6510\) & \(6250\) & \(1000\) & \(1299\) & \(6250\) \\
+		\textbf{Bandwidth / pulse width} & (\si{\mega\hertz} / \(\upmu\si{\second})\) & \(15\)   & \(6\)    & \(10\)   & \(5\)    & \(0.5\)  \\
+		\textbf{Range resolution}        & (\si{\metre})                              & \(10\)   & \(25\)   & \(15\)   & \(30\)   & \(75\)   \\
+
+		\textbf{Transmit power}          & (\si{\deci\belm})                          & \(25\)   & \(30\)   & \(27\)   & \(23\)   & \(61.8\) \\
+		\textbf{Antenna gain}            & (\si{\deci\beli})                          & \(52\)   & \(54\)   & \(57\)   & \(55\)   & \(50\)   \\
+		\textbf{Beamwidth}               & (\degree)                                  & \(0.43\) & \(0.4\)  & \(0.18\) & \(0.15\) & \(0.5\)  \\
+
+		\textbf{Noise figure}            & (\si{\deci\bel})                           & \(5.3\)  & \(8\)    & \(5.5\)  & \(5\)    & \(9\)    \\
+
+		\textbf{Weather constant}        & (\si{\deci\belm})                          & \(119\)  & \(132\)  & \(126\)  & \(119\)  & \(162\)  \\
+	\end{tabular}
+	\caption{Parameters for various radar systems.}
+	\label{tbl:RadarSystems}
+\end{table}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{sensitivity-2}
+	\caption{Predicted minimum detectable reflectivity curves using parameters for the radars described in Table \ref{tbl:RadarSystems}.
+Assumes a desired signal-to-noise ratio of \(1\), an ambient temperature of \SI{290}{\kelvin}, and \(\abs{K}^2 = 0.846\) which is appropriate for cloud particles in the water phase and an incident wavelength of \SI{3.2}{\milli\metre} (\SI{94}{\giga\hertz}).\supercite{ComplexIndexOfRefraction} The main region of interest for cloud radars is highlighted in grey.
+The \SI{1}{\second} non-coherent averaging curves assumes a \(\sqrt{N}\) improvement to the signal-to-noise ratio, where \(N\) is the number of chirps averaged together.
+(Own work)}
+	\label{fig:Sensitivity}
+\end{figure}
+
+\section{Project work}
+The St Andrews radar software needs to be updated to allow for averaging, extraction of Doppler moments, and real-time output.
+Also, calibration and some outdoor testing needs to be performed, in particular assessing the effect of ambient temperature on radar performance.
+\paragraph{Signal averaging.} Averaging of range profiles reduces noise and increases sensitivity to low reflectivity clouds such as thin cirrus.
+Figure \ref{fig:Sensitivity} shows that without averaging the radar will be unable to detect any clouds above \SI{2}{\kilo\metre}.
+\paragraph{Doppler moments.} Extraction of Doppler moments provides meteorologists with further information on the microphysical processes behind cloud formation.
+\paragraph{Real-time output.} Real-time saving in netCDF,\supercite{NetCDFFormat} a format widely used by meteorologists.
+This would allow for offline data processing.
+Most of the radars in Table \ref{tbl:RadarSystems} support exporting data in netCDF format.
+\paragraph{Effect of ambient temperature.} Changes in ambient temperature could affect the radar performance.
+Solid-state devices are particularly vulnerable to thermal drift.
+Thermal sensors in the radar enclosure will record the ambient temperature over a long period of time which can be correlated to radar performance.
+\paragraph{Cross-check results with disdrometer.} Time permitting, a disdrometer located next to the radar can be used to record the drop-size distribution while raining.
+From this, the expected reflectivity can be calculated and compared to the output from the radar.
+
+\section{Conclusions}
+This article provided an introduction to millimetre wave cloud profiling radar, covering the principes of range, velocity, and reflectivity measurement using FMCW-Doppler processing.
+A select few modern cloud profiling radars were compared by their sensitivity.
+Cloud radars, particularly at \SI{94}{\giga\hertz}, will remain an invaluable tool in the study of clouds.
+Low-cost millimetre wave FMCW-Doppler radars could mean wider deployment of cloud radars, improving weather forecasts and climate models.
+
 \printbibliography

### 2022-04-01 report/report.tex
Use oneside instead of twoside
Update report

@@
-\documentclass[sotoncolour]{uosthesis}  % Use the Thesis Style with custom link colour
-\graphicspath{{../figures/}}            % Location of your graphics files
-\usepackage[round]{natbib}              % Use Natbib style for the refs.
-\usepackage{bibentry}                   % Use bibentry for prepublished works
-\nobibliography*                        % Use bibentry for prepublished works
-\usepackage{attrib}                     % Use the attrib package for quotations
-\hypersetup{colorlinks=true}            % Set to false for black/white printing
-\hypersetup{pdfstartpage=1}             % Set first page to skip copyright declaration
+\documentclass{article}
 
-\usepackage{blindtext}                  % TODO: removeme
+\usepackage[a4paper, margin=1in]{geometry}
+\usepackage[onehalfspacing]{setspace} % Correct 1.5 line spacing
 
-%% ----------------------------------------------------------------
-%% --------------------THESIS/DOC INFORMATION ---------------------
-%\faculty     {Faculty of Science}
-%\FACULTY     {\MakeUppercase{\facname}}
-\department  {School of Physics and Astronomy}
-\DEPARTMENT  {\MakeUppercase{\deptname}}
-%\group       {[Group name]}
-%\GROUP       {\MakeUppercase{\groupname}}
-\title       {BSc Project Report}
-\modulename  {PH4111}
-\authors     {180014855}
-\date        {\today}
+\usepackage{graphicx}  % Figures
+\graphicspath{{./figures/}}
+
+\usepackage{url}
+\usepackage[pdfusetitle]{hyperref}
+\usepackage{titlesec}      % Modify title/section/chapter commands
+\usepackage{mathtools}     % Various maths related commands
+\usepackage{gensymb}       % \degree symbol
+\usepackage[thinc]{esdiff} % Derivatives
+\usepackage{booktabs}      % \toprule, etc., in tables
+\usepackage{doi}           % support DOI links in bibliography
+\usepackage{wrapfig}       % figures in text
+
+\usepackage{fontspec}      % Fonts
+\usepackage{helvet}
+\usepackage{newpxtext,newpxmath}
+\defaultfontfeatures{Scale=MatchLowercase, Ligatures=TeX}
+
+% SI units
+\usepackage{siunitx}
+\sisetup{separate-uncertainty=true,number-mode=text,detect-weight=true}
+\DeclareSIUnit\belm{Bm}
+\DeclareSIUnit\belw{BW}
+\DeclareSIUnit\beli{Bi}
+\DeclareSIUnit\belz{BZ}
+
+% https://tex.stackexchange.com/a/43009
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+% Caption figures
+\usepackage{caption}
+\DeclareCaptionFont{captionlabelfont}{\bfseries \sffamily}
+\DeclareCaptionFont{captiontextfont}{\sffamily}
+\captionsetup{labelfont=captionlabelfont, textfont=captiontextfont}
+
+% Change footnote style
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
+% Fancy header/footer
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\renewcommand{\sectionmark}[1]{\markright{\thesection . #1}}
+\fancyhf{}
+\lhead{\fancyplain{}{\thepage}}
+\rhead{\fancyplain{}{\textit{\rightmark}}}
+
+% Bibliography
+\usepackage[backend=biber, style=ieee, natbib=true,
+			url=false, isbn=true, doi=true,
+			eprint=false, urldate=long]{biblatex}
+%\addbibresource{references-old.bib}
+\addbibresource{references.bib}
+
+% biblatex IEEE style leaves empty parentheses when there is no date/year field.
+% Since there are no date fields for many online resources, we use
+%   https://tex.stackexchange.com/a/151264
+% to stop these parentheses from being generated if there is no date field.
+\usepackage{xpatch}
+\xpatchbibdriver{online}
+{\printtext[parens]{\usebibmacro{date}}}
+{\iffieldundef{year}
+	{}
+	{\printtext[parens]{\usebibmacro{date}}}}
+{}
+{\typeout{There was an error patching biblatex-ieee (specifically, ieee.bbx's @online driver)}}
+
+\renewcommand{\descriptionlabel}[1]{\hspace*{\labelsep}\spacedlowsmallcaps{#1}}
+
+\titlespacing*{\chapter}{0pt}{1\baselineskip}{1.2\baselineskip}
+\titlespacing*{\section}{0pt}{1.25\baselineskip}{1\baselineskip} 
+\titlespacing*{\subsection}{0pt}{1.25\baselineskip}{1\baselineskip}
+\titlespacing*{\paragraph}{0pt}{1\baselineskip}{1\baselineskip}
+
+% Fix for missing µ in siunitx ???
+% https://tex.stackexchange.com/a/428215
+\sisetup{math-micro=\text{µ},text-micro=µ}
+
+\newcommand\mytitle    {Millimetre-Wave Cloud Profiling Radar}
+\newcommand\mysubtitle {Project Report}
+\newcommand\myauthor   {180014855}
+\newcommand\mydate     {\today}
+\newcommand\mymodule   {PH4111}
+\newcommand\mywordcount{2300}
+
+\title {\mytitle}
+\author{\myauthor}
+\date  {\mydate}
+
+%\usepackage[acronym,nonumberlist]{glossaries}
+%\usepackage[acronym,nonumberlist]{glossaries-extra}
+
+\usepackage[nopostdot, toc, nogroupskip, nomain, indexonlyfirst, acronym, symbols, style=long4col, stylemods={longextra}, nonumberlist]{glossaries-extra}
+
+\makeglossaries
+
+%\setabbreviationstyle[acronym]{long-short}
+
+\newacronym{ac:daq}{DAQ}{Data acquisition}
+\newacronym{ac:simd}{SIMD}{Single instruction, multiple data}
+\newacronym{ac:cpr}{CPR}{Cloud profiling radar}
+\newacronym{ac:fmcw}{FMCW}{Frequency-modulated continuous wave}
+\newacronym{ac:netcdf}{NetCDF}{Network common data form}
+\newacronym{ac:openmp}{OpenMP}{Open multi-processing}
+\newacronym{ac:adc}{ADC}{Analogue to digital converter}
+\newacronym{ac:dds}{DDS}{Direct digital synthesiser}
+\newacronym{ac:dft}{DFT}{Discrete Fourier transform}
+\newacronym{ac:fftw}{FFTW}{Fastest Fourier Transform in the West}
+\newacronym{ac:mkl}{Intel MKL}{Intel Math Kernel Library}
+\newacronym{ac:snr}{SNR}{Signal-to-noise ratio}
+\newacronym{ac:if}{IF}{Intermediate frequency}
+\newacronym{ac:cpi}{CPI}{Coherent processing interval}
+\newacronym{ac:cpu}{CPU}{Central processing unit}
+
+%\newglossaryentry{busywaiting}
+%{
+%	name=formula,
+%	description={A mathematical expression}
+%}
+
+\glsaddall
 
 \begin{document}
-%% ------------------ FRONT MATTER ORGANISATION -------------------
-\pagenumbering{gobble} % removes page number
-\raggedright           % Set the style to left justification, remove for fill justification
 
-\frontmatter
-\maketitle
+\begin{titlepage}
+	\centering
+	{\includegraphics[width=0.3\textwidth]{uos-logo}}
+	\par
+	{\LARGE\bfseries University of St Andrews\par}
+	{\LARGE School of Physics and Astronomy\par}
+	\vspace{1.5cm}
+	{\huge\bfseries\mytitle\par}
+	{\Large\mysubtitle\par}
+	\vspace{2cm}
+	{\Large\myauthor\par}
+	{\large\textbf{Module:} \mymodule\par}
+	{\large\textbf{Word count:} \mywordcount\par}
+	\vfill
+	{\large\today\par}
+\end{titlepage}
+
 \begin{abstract}
-\input{00-abstract}
+	Insert abstract here.
 \end{abstract}
-\pdfbookmark[0]{\contentsname}{toc} % Add pdf bookmark for contents page for navigation
+
 \tableofcontents
-\listoffigures
-\listoftables
-\addtotoc{Listings} % The list of listings does not, by default, appear in the ToC
-\lstlistoflistings
-\listofaddmaterial
-\mainmatter
-%% ------------------ MAIN MATTER (CONTENT) --------------------
-\input{10-introduction}
-\input{30-experiment}
-\input{50-results}
-\input{70-conclusions}
 
-\appendix
-\input{90-appendix-a}
-\backmatter
-\bibliographystyle{plainnat}
-\bibliography{references}
-\chapter{Bibliography}
-To use bibliography as well as the references section use the \texttt{multibbl} package.
+\section{Introduction}
+
+\section{Signal processing theory}
+\subsection{FMCW-Doppler radar}
+The main
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{slow-fast-time}
+	\caption{Fast-time vs slow-time. Adapted from \cite{SlowFastTimeFig}.}
+	\label{fig:SlowFastTime}
+\end{figure}
+
+\subsection{Signal averaging}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{sensitivity}
+	\caption{Radar sensitivity  (Own work).}
+	\label{fig:SlowFastTime}
+\end{figure}
+
+\subsection{Doppler moments}
+
+\section{Requirements}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{mark-1-rain}
+	\caption{Screenshot of Mark I user interface, taken during precipitation.}
+	\label{fig:Mark1Rain}
+\end{figure}
+
+\section{Design and implementation}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{signal-processing-diagram}
+	\caption{Simplified block diagram illustrating key signal processing steps. (Own work)}
+	\label{fig:SignalProcessingDiagram}
+\end{figure}
+
+\subsection{Data acquisition}
+\subsubsection{Double buffering}
+To ensure real-time output, a double buffering approach is used.
+One buffer is used to store the incoming frame and another stores the previously acquired frame 
+While the next frame is being acquired, the most recent frame is processed.
+
+\subsubsection{Alternatives to double buffering}
+The approach in Mark II used one acquisition thread and one processing thread.
+The acquisition thread repeatedly acquires data and appends it to a thread-safe queue, which the processing thread pulls from
+
+The main issue with this approach is the acquisition thread wastes \acrshort{ac:cpu} time waiting for the frame to be acquired and transferred to memory
+
+\subsubsection{Testing}
+To facilitate testing the software, a mock implementation of the \acrshort{ac:daq} was created.
+
+\subsection{FMCW-Doppler processing}
+
+\subsubsection{Testing}
+
+\subsection{Averaging}
+\subsection{Doppler moments}
+
+\section{Results}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{working-cloud}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingCloud}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{working-hail}
+	\caption{Screenshot of the new user interface, showing hail.}
+	\label{fig:WorkingHail}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{working-heavy-rain-snow}
+	\caption{Screenshot of the new user interface, showing heavy rain and/or sleet.}
+	\label{fig:WorkingHeavyRainSnow}
+\end{figure}
+
+\subsection{Performance}
+Compare processing time of previous software
+
+\section{Future work}
+\subsection{Effect of ambient temperature}
+\subsection{NetCDF}
+
+\subsection{Performance improvements}
+\subsubsection{Multithreading}
+\subsubsection{OpenMP}
+\subsubsection{SIMD}
+Single instruction, multiple data (SIMD) is another type of parallel processing that
+
+\section{Conclusions}
+
+\clearpage
+\printglossary
+\printbibliography
+
 \end{document}
-%% ----------------------------------------------------------------

### 2022-04-05 report/report.tex
Update

@@
 \defaultfontfeatures{Scale=MatchLowercase, Ligatures=TeX}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 
-\usepackage[nopostdot, toc, nogroupskip, nomain, indexonlyfirst, acronym, symbols, style=long4col, stylemods={longextra}, nonumberlist]{glossaries-extra}
+\usepackage[nopostdot, toc, nogroupskip, nomain, indexonlyfirst, acronym, symbols, style=long4col, stylemods={longextra}, nonumberlist, automake]{glossaries-extra}
 
@@
 \subsection{FMCW-Doppler radar}
-The main
+Explain fast and slow time / range and velocity determination. Range and velocity resolution.
+
+Is it worth including fig \ref{fig:Chirp}?
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{chirp}
+	\caption{Chirp (own work)}
+	\label{fig:Chirp}
+\end{figure}
 
@@
 \subsection{Signal averaging}
+Explain with signal averaging we can get \(\sqrt{N}\) improvement in SNR, why that's necessary to detect clouds
+
 \begin{figure}
 	\centering
-	\includegraphics[width=\textwidth]{sensitivity}
+	\includegraphics[width=0.6\textwidth]{sensitivity}
 	\caption{Radar sensitivity  (Own work).}
@@
 \subsection{Doppler moments}
+I wonder if it's worth removing this section since I didn't quite get Doppler moments working
 
 \section{Requirements}
+Explain current state of Mark I and Mark II software
 
@@
 To ensure real-time output, a double buffering approach is used.
-One buffer is used to store the incoming frame and another stores the previously acquired frame 
-While the next frame is being acquired, the most recent frame is processed.
+One buffer is used to store the incoming frame and another stores the most recently acquired frame.
+While the next frame is being acquired, the most recent frame is processed and displayed. The algorithm is shown in Alg. \ref{alg:DoubleBuffering}.
+
+\begin{algorithm}
+	\centering
+	\begin{algorithmic}
+		\State acquire frame asynchronously into buffer $A$
+		\While {keep acquiring data}
+		\State wait for previous acquisition to finish
+		\State acquire frame asynchronously into buffer $B$
+		\State process frame in buffer $A$
+		\State display processed frame
+		\State swap $A$ and $B$ pointers
+		\EndWhile
+	\end{algorithmic}
+	\caption{Double buffering approach.}\label{alg:DoubleBuffering}
+\end{algorithm}
 
@@
 The approach in Mark II used one acquisition thread and one processing thread.
-The acquisition thread repeatedly acquires data and appends it to a thread-safe queue, which the processing thread pulls from
+The acquisition thread repeatedly acquires and appends frames to a thread-safe queue, which the processing thread pulls from.
 
-The main issue with this approach is the acquisition thread wastes \acrshort{ac:cpu} time waiting for the frame to be acquired and transferred to memory
+The main issue with this approach is the acquisition thread wastes \acrshort{ac:cpu} time waiting for the frame to be acquired and transferred to memory.
 
-\subsubsection{Testing}
-To facilitate testing the software, a mock implementation of the \acrshort{ac:daq} was created.
+\begin{algorithm}
+	\begin{minipage}{0.48\linewidth}
+		\begin{algorithmic}
+			\While {keep acquiring data}
+			\State acquire frame into buffer
+			\State wait for previous acquisition to finish
+			\State copy into thread safe queue
+			\EndWhile
+		\end{algorithmic}
+	\end{minipage}
+	\begin{minipage}{0.48\linewidth}
+		\begin{algorithmic}
+			\While {keep acquiring data}
+			\State copy next frame in thread-safe queue
+			\State process frame
+			\State display processed frame
+			\EndWhile
+		\end{algorithmic}
+	\end{minipage}
+	\caption{Acquisition (left) and processing (right) threads.}\label{alg:TwoThreads}
+\end{algorithm}
+
+The double buffering approach uses only two buffers, which avoids unnecessary copying of data between threads and the additional overhead of using a thread-safe queue.
 
 \subsection{FMCW-Doppler processing}
+The software uses a third-party library, \acrshort{ac:fftw} v3\cite{FFTWv3}, to ensure correctness and good performance in the two discrete Fourier transform steps in the FMCW-Doppler process.
 
-\subsubsection{Testing}
+Newer versions of LabWindows CVI use \acrshort{ac:fftw} behind the scenes, however the interface is not as flexible.
+\acrshort{ac:fftw} supports multiple transforms of non-unit stride,\footnote{Stride is the number of memory locations between each successive element in an array.} allowing one to easily perform multiple transforms along different dimensions.
+This is particularly useful for the column-wise slow-time transform, because it means the data does not need to be transposed before transforming.
+
+The window functions available in the new software are flat-top, Han, Blackman, and Blackman-Harris.
+
+\subsubsection{Averaging}
+In each frame, two averaging processes take place.
+Averaging of power spectra is done over each chirp.
+For a frame containing \(256\) \acrshort{ac:cpi}s each containing \(64\) chirps, this amounts to \(256 \times 64 = \)
+
+\subsection{Testing}
+To facilitate testing the software, a mock implementation of the \acrshort{ac:daq} was created.
+Raw data (\acrshort{ac:adc} integers) saved by the Mark II can be loaded by the mock implementation and used as if the data was just acquired.
+This feature is extremely useful for reproducible debugging and testing.
+A few snapshots of rain data were saved and used to test the new code when the weather was too clear.
+
+A signal generator was attached to the second input channel of the \acrshort{ac:daq} card.
+Checking to see if the input power matches the peak value in the fast-time power spectrum provides confirmation that any corrections or scaling performed during the fast-time processing is correct.
+
+Setting the input frequency to be slightly off bin centre introduces spectral leakage (Fig.
+\ref{fig:WindowNone}) Fig.
+\ref{fig:WindowBMH} shows the effect of applying the Blackman-Harris window is as expected.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{window-none}
+	\caption{Fast-time power spectrum without windowing.}
+	\label{fig:WindowNone}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{window-bmh}
+	\caption{Fast-time power spectrum with Blackman-Harris windowing.}
+	\label{fig:WindowBMH}
+\end{figure}
 
 \subsection{Averaging}
-\subsection{Doppler moments}
+How is averaging implemented? Not much to say here really
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{working-cloud}
+	\includegraphics[width=0.4\textwidth]{working-cloud_range-doppler}
 	\caption{Screenshot of the new user interface.}
-	\label{fig:WorkingCloud}
+	\label{fig:WorkingCloudRangeDoppler}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{working-hail}
-	\caption{Screenshot of the new user interface, showing hail.}
-	\label{fig:WorkingHail}
+	\includegraphics[width=\textwidth]{working-cloud_power-spect}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingCloudPowerSpectrum}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{working-heavy-rain-snow}
-	\caption{Screenshot of the new user interface, showing heavy rain and/or sleet.}
-	\label{fig:WorkingHeavyRainSnow}
+	\includegraphics[width=0.4\textwidth]{working-hail_range-doppler}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingHailRangeDoppler}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{working-hail_power-spect}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingHailPowerSpectrum}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.4\textwidth]{working-heavy-rain-sleet_range-doppler}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingHeavyRainSnowRangeDoppler}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{working-heavy-rain-sleet_power-spect}
+	\caption{Screenshot of the new user interface.}
+	\label{fig:WorkingHeavyRainSnowPowerSpectrum}
 \end{figure}
@@
 \section{Future work}
+\subsection{Doppler moments}
+Extracting the Doppler spectrum from the averaged range-Doppler data has already been implemented along with UI controls for displaying Doppler moments, however the formulas used for determining the moments are incorrect.
+
 \subsection{Effect of ambient temperature}
@@
 \subsubsection{Multithreading}
-\subsubsection{OpenMP}
+An easy way of using multithreading is \acrshort{ac:openmp}
+[Briefly mention how OpenMP can be used to parallelise loops]
+
 \subsubsection{SIMD}
-Single instruction, multiple data (SIMD) is another type of parallel processing that
+Single instruction, multiple data (SIMD) is another type of parallel processing where a single instruction operates simultaneously on multiple pieces of data.
+\acrshort{ac:fftw} uses this extensively.
+Many of the steps in the FMCW-Doppler process are adding or multiplying rows or columns by the same constants which makes \acrshort{ac:simd} ...
 

### 2022-04-07 report/report.tex
Update

@@
 \newacronym{ac:cpu}{CPU}{Central processing unit}
+\newacronym{ac:cvi}{CVI}{C for Virtual Instrumentation, an ANSI C environment designed by National Instruments.}
+\newacronym{ac:fft}{FFT}{Fast Fourier transform}
+\newacronym{ac:vla}{VLA}{Variable length array}
 
-%\newglossaryentry{busywaiting}
-%{
-%	name=formula,
-%	description={A mathematical expression}
-%}
+\newglossaryentry{gl:fast-time}
+{
+	name={fast time},
+	description={On the time scale of one chirp}
+}
+
+\newglossaryentry{gl:slow-time}
+{
+	name={slow time},
+	description={On the time scale of multiple chirps}
+}
 
@@
 \tableofcontents
+\clearpage
+\printglossary
 
@@
 
+\footnote{The code is available on GitHub.\supercite{Code}}
+
 \section{Signal processing theory}
 \subsection{FMCW-Doppler radar}
-Explain fast and slow time / range and velocity determination. Range and velocity resolution.
+\acrshort{ac:fmcw} radar emit consecutive chirps - signals whose frequency is linearly modulated by sawtooth waves.
+The reflected chirp arrives at a time \(\Delta t\) after emission, leading to a phase difference as illustrated in Fig.
+\ref{fig:Chirp}.
+The transmitted and received signals are mixed (Fig.
+\ref{fig:RadarDiagram}) and their intermediate frequency (\acrshort{ac:if}, essentially the difference frequency) is extracted.
+The target range relates to the time delay and hence the intermediate frequency \(f_{IF}\) by
+\begin{equation}
+	r = \frac{c \Delta t}{2} = \frac{c f_{IF} T_c}{2 B},
+\end{equation}
+where \(r\) is the distance from the radar and \(T_c\) is the chirp duration.\supercite{TIFMCWDoppler}
+In practice, there are many received signals, thus one performs a discrete Fourier transform of the \acrshort{ac:if} signal to obtain a range profile, known as a range-\acrshort{ac:fft} or \textit{fast time} \acrshort{ac:fft} because of the short timescale (and high sampling rate) over which samples are taken.
 
-Is it worth including fig \ref{fig:Chirp}?
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{chirp}
-	\caption{Chirp (own work)}
+	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform. (Own work)}
 	\label{fig:Chirp}
@@
 	\centering
-	\includegraphics[width=\textwidth]{slow-fast-time}
-	\caption{Fast-time vs slow-time. Adapted from \cite{SlowFastTimeFig}.}
-	\label{fig:SlowFastTime}
+	\includegraphics[width=\textwidth]{radar-diagram}
+	\caption{Simplified radar system diagram.\supercite{Radar}}
+	\label{fig:RadarDiagram}
 \end{figure}
+
+To obtain velocity information one extracts the phase change in each range bin across multiple consecutive chirps by performing a Doppler-\acrshort{ac:fft} or \textit{slow time} \acrshort{ac:fft}.
+The phase difference \(\delta\) relates to the target velocity \(v\) by\supercite{TIFMCWDoppler}
+\begin{equation}
+	\delta = \frac{4 \pi v T_c}{\lambda}.
+\end{equation}
+
+The sequence of chirps is known as a coherent processing interval (\acrshort{ac:cpi}), the duration of which determines the velocity resolution \(v_{res}\) by
+\begin{equation}
+	v_{res} = \frac{\lambda}{2 T_f},
+\end{equation}
+where \(T_f\) is the \acrshort{ac:cpi} duration.
+
+Each \acrshort{ac:cpi} can be thought of as a matrix where each row represents the fast-time samples.
+The fast-time \acrshort{ac:fft}s are performed row-by-row to get several range profiles and, afterwards, the slow-time \acrshort{ac:fft}s are performed column-by-column to obtain the velocity spectra.
 
@@
 	\caption{Radar sensitivity (Own work).}
-	\label{fig:SlowFastTime}
+	\label{fig:Sensitivity}
 \end{figure}
@@
 \subsection{Doppler moments}
-I wonder if it's worth removing this section since I didn't quite get Doppler moments working
+Statistical properties of the velocity spectrum are of great interest to meteorologists. In particular, the mean, variance, skew, and kurtosis ...
 
 \section{Requirements}
-Explain current state of Mark I and Mark II software
+There are two software implementations to date, named Mark I and Mark II.
+Mark I
+
+Mark II supports real-time data acquisition (see Sec.
+\ref{sc:AltToDblBuf}) and saving of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}.
+
+\subsection{User interface and hardware control}
+It should also be noted that these implementations exclusively deal with the data acquisition and processing aspect of radar software.
+The hardware control runs in a separate process.
+One of the extra project goals is to add a hardware control panel containing controls for bandwidth, chirp or continuous wave mode, transmitter on/off as well as output from various sensors.
+The panel could be switched between engineering and operational mode, where operational mode hides low-level controls and replaces them with more intuitive controls, such as range resolution instead of bandwidth.
+The panel would also contain controls for adjusting averaging time and velocity resolution.
 
@@
 One buffer is used to store the incoming frame and another stores the most recently acquired frame.
-While the next frame is being acquired, the most recent frame is processed and displayed. The algorithm is shown in Alg. \ref{alg:DoubleBuffering}.
+While the next frame is being acquired, the most recent frame is processed and displayed.
+The algorithm is shown in Alg.
+\ref{alg:DoubleBuffering}.
+Double buffering guarantees continuous real-time acquisition only if the processing time is less than the acquisition time.
 
@@
 
-\subsubsection{Alternatives to double buffering}
+\subsubsection{Alternatives to double buffering}\label{sc:AltToDblBuf}
 The approach in Mark II used one acquisition thread and one processing thread.
@@
 \subsection{FMCW-Doppler processing}
-The software uses a third-party library, \acrshort{ac:fftw} v3\cite{FFTWv3}, to ensure correctness and good performance in the two discrete Fourier transform steps in the FMCW-Doppler process.
+The software uses a third-party library, \acrshort{ac:fftw} v3\cite{FFTWv3}, for the two discrete Fourier transform steps in the FMCW-Doppler process.
 
-Newer versions of LabWindows CVI use \acrshort{ac:fftw} behind the scenes, however the interface is not as flexible.
+Newer versions of LabWindows \acrshort{ac:cvi} use \acrshort{ac:fftw} behind the scenes, however the interface is not as flexible.
 \acrshort{ac:fftw} supports multiple transforms of non-unit stride,\footnote{Stride is the number of memory locations between each successive element in an array.} allowing one to easily perform multiple transforms along different dimensions.
 This is particularly useful for the column-wise slow-time transform, because it means the data does not need to be transposed before transforming.
+In \acrshort{ac:cvi}, the \acrshort{ac:fft} routines are limited to a single contiguous 1D array at a time.
 
-The window functions available in the new software are flat-top, Han, Blackman, and Blackman-Harris.
+In \acrshort{ac:fftw}, \textit{plans} are created
+
+The window functions available in the new software are flat-top, Hann, Blackman, and Blackman-Harris.
 
@@
 Averaging of power spectra is done over each chirp.
-For a frame containing \(256\) \acrshort{ac:cpi}s each containing \(64\) chirps, this amounts to \(256 \times 64 = \)
+For a frame containing \(256\) \acrshort{ac:cpi}s each containing \(64\) chirps, this amounts to \(16384\) chirps averaged together.
 
@@
 \subsection{Performance}
-Compare processing time of previous software
+The results in Tbl.
+\ref{tbl:ProcTime} show that the new code has continuous, real time acquisition.
+One \acrshort{ac:cpi} containing \(64\) chirps each with \(2048\) samples lasts for \(\SI{19.7}{\milli\second}\), which is more than the processing time of \(\SI{13.9(1)}{\milli\second}\).
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		        & Processing time             \\
+		\hline
+		Mark II & \SI{67.6(6)}{\milli\second} \\
+		\hline
+		New     & \SI{13.9(1)}{\milli\second} \\
+		\hline
+	\end{tabular}
+	\caption{Processing time of Mark II vs new code.
+Measured as the time taken to process one \acrshort{ac:cpi} (\(64\) chirps, \(2048\) samples).
+For new code this also includes power spectrum averaging and Doppler moment extraction.
+Number of samples: \(400\).
+Both built using \acrshort{ac:cvi} v19.0.0.
+Release build.}
+	\label{tbl:ProcTime}
+\end{table}
+
+There are several reasons for the speed improvements in the new code.
+Both the Mark I and Mark II frequently copy data into temporary arrays while processing, which is avoided in the new code.
+In addition, these temporary arrays are variable-length (\acrshort{ac:vla}s) which are generally slower than arrays with a size known at compile-time or dynamically allocated arrays.
+The new code leverages \acrshort{ac:fftw}'s advanced interface to \acrshort{ac:fft} the entire 2D \acrshort{ac:cpi} array in one go.
+Since \acrshort{ac:fftw} knows the dimensions of the input it might be using optimisations suited for multidimensional transforms.
 
 \section{Future work}
+\subsection{Calibration}
+Currently the output power is in \(\si{\deci\belm}\) rather than \(\si{\deci\belz}\).
+Since the conversion to \(\si{\deci\belz}\) is dependent on bandwidth and the hardware control was not fully implemented, it was decided to not convert to \(\si{\deci\belz}\) yet.
+
 \subsection{Doppler moments}
-Extracting the Doppler spectrum from the averaged range-Doppler data has already been implemented along with UI controls for displaying Doppler moments, however the formulas used for determining the moments are incorrect.
+Extracting the Doppler spectrum from the averaged range-Doppler data has already been implemented along with UI controls for displaying Doppler moments, however the results are wildly incorrect.
+
+the formulas used for determining the moments are incorrect.
 
@@
 \subsubsection{Multithreading}
-An easy way of using multithreading is \acrshort{ac:openmp}
-[Briefly mention how OpenMP can be used to parallelise loops]
+Many of the calculations in the \acrshort{ac:fmcw}-Doppler process are highly parallel and are performed on large
+
+An easy way of parallelising loops with is to use \acrshort{ac:openmp}
 
 \subsubsection{SIMD}
-Single instruction, multiple data (SIMD) is another type of parallel processing where a single instruction operates simultaneously on multiple pieces of data.
+Single instruction, multiple data (\acrshort{ac:simd}) is another type of parallel processing where a single instruction operates simultaneously on multiple pieces of data.
 \acrshort{ac:fftw} uses this extensively.
-Many of the steps in the FMCW-Doppler process are adding or multiplying rows or columns by the same constants which makes \acrshort{ac:simd} ...
+Many of the steps in the \acrshort{ac:fmcw}-Doppler process are adding or multiplying rows or columns by the same constants which makes \acrshort{ac:simd} highly effective.
 
@@
 \clearpage
-\printglossary
 \printbibliography

### 2022-04-08 report/report.tex
Update

@@
 
+Science is often highly collaborative. Please clarify here which parts of the work reported have been done by you and which parts include the work of others.
+
+For example, this might include provision of simulation or analysis codes which you utilised or modified, provision of experimental data to analyse, collaborations wit others in performing new measurements, if you built up things from scratch in your project or started from pre-existing setups, and others.
+Providing this information helps clarify the scope and focus of your project work.
+
+\begin{itemize}
+	\item Mark I code was supplied by Dr Duncan Robertson.
+	\item Mark II code was developed by Dr Samiur Rahman.
+	\item New code is a complete rewrite from scratch.
+\end{itemize}
+
+\clearpage
+\setcounter{page}{1}
+
 \begin{abstract}
@@
 	\includegraphics[width=\textwidth]{chirp}
-	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and their difference frequency (IF). Right: illustration of TX chirp waveform. (Own work)}
+	\caption{Left: transmitted (TX) and received (RX) sawtooth chirps and the intermediate frequency (\acrshort{ac:if}). Right: illustration of TX chirp waveform. (Own work)}
 	\label{fig:Chirp}
@@
 \subsection{Signal averaging}
+In this context, a \textit{frame} is a sequence of \acrshort{ac:cpi}s to be averaged together.
+
 Explain with signal averaging we can get \(\sqrt{N}\) improvement in SNR, why that's necessary to detect clouds
@@
 \section{Requirements}
+\subsection{Current state of radar software}
 There are two software implementations to date, named Mark I and Mark II.
+
 Mark I
@@
 \ref{sc:AltToDblBuf}) and saving of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}.
+While the data acquisition is real-time, it is not continuous.
 
@@
 The panel would also contain controls for adjusting averaging time and velocity resolution.
+
+\subsection{Project goals}
+The main project goals are:
+\paragraph{Continuous real-time processing.} Ensure no frames are dropped and the processing is real-time.
+
+\paragraph{User interface} Combine hardware control and sensors into new code.
+Implement two different modes of display: operational (range and velocity resolution, etc.) and engineering (bandwidth, etc.).
+Add plot showing reflectivity as a function of range and time.
+
+\paragraph{Signal averaging.} Implement averaging of power spectra and range-Doppler data to significantly improve sensitivity to clouds.
+
+\paragraph{Doppler moments.} Display velocity spectrum for a particular range bin and calculate its moments.
+
+\paragraph{Calibration.} Convert output from \(\si{\deci\belm}\) to \(\si{\deci\belz}\).
+
+\paragraph{Effect of ambient temperature.} Sensors inside the radar enclosure can record the temperature. Record temperature over a long period of time and correlate to radar performance.
+
+\paragraph{Cross-check results with a disdrometer.} Use adjacent disdrometer to record the drop-size distribution while raining.
+The reflectivity can then be calculated and compared to the radar output.
 
@@
 \subsection{FMCW-Doppler processing}
-The software uses a third-party library, \acrshort{ac:fftw} v3\cite{FFTWv3}, for the two discrete Fourier transform steps in the FMCW-Doppler process.
+The software uses a third-party library, \acrshort{ac:fftw} v3 (\cite{FFTWv3}), for the two discrete Fourier transform steps in the FMCW-Doppler process.
 
@@
 In \acrshort{ac:cvi}, the \acrshort{ac:fft} routines are limited to a single contiguous 1D array at a time.
-
-In \acrshort{ac:fftw}, \textit{plans} are created
 

### 2022-04-08 report/report.tex
Final update

@@
 \newacronym{ac:vla}{VLA}{Variable length array}
+\newacronym{ac:dc}{DC}{Direct current (zero frequency)}
 
@@
 
-\glsaddall
+%\glsaddall
 
@@
 	{\large\textbf{Module:} \mymodule\par}
-	{\large\textbf{Word count:} \mywordcount\par}
+%	{\large\textbf{Word count:} \mywordcount\par}
 	\vfill
@@
 
+\thispagestyle{empty}
 \clearpage
@@
 \begin{abstract}
-	Insert abstract here.
+	This report details recent upgrades to the cloud profiling radar software, including continuous real-time data acquisition, signal averaging, and extraction of statistical properties from the velocity spectrum.
+Performance is compared to two previous implementations.
 \end{abstract}
@@
 \section{Introduction}
-
-\footnote{The code is available on GitHub.\supercite{Code}}
+The current cloud profiling radar code is of limited usefulness to meteorologists due to low sensitivity of clouds, lack of continuous real-time display, 
+This report details the implementation of these new features and the construction of new, modular design to the cloud profiling radar software.\footnote{The code is available on GitHub.\supercite{Code}}
 
@@
 
-To obtain velocity information one extracts the phase change in each range bin across multiple consecutive chirps by performing a Doppler-\acrshort{ac:fft} or \textit{slow time} \acrshort{ac:fft}.
+To obtain velocity information one extracts the phase change in each range bin across multiple consecutive chirps by performing a Doppler-\acrshort{ac:fft} or \textit{slow time} \acrshort{ac:fft}.\supercite{POMRDopplerProcessing}
 The phase difference \(\delta\) relates to the target velocity \(v\) by\supercite{TIFMCWDoppler}
@@
 In this context, a \textit{frame} is a sequence of \acrshort{ac:cpi}s to be averaged together.
-
-Explain with signal averaging we can get \(\sqrt{N}\) improvement in SNR, why that's necessary to detect clouds
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\textwidth]{sensitivity}
-	\caption{Radar sensitivity (Own work).}
-	\label{fig:Sensitivity}
-\end{figure}
+Non-coherent averaging will increase the signal-to-noise ratio (\acrshort{ac:snr}) and hence improve sensitivity to clouds.\supercite{POMRNonCoherentAveraging}
 
 \subsection{Doppler moments}
-Statistical properties of the velocity spectrum are of great interest to meteorologists. In particular, the mean, variance, skew, and kurtosis ...
+Statistical properties of the velocity spectrum are of great interest to meteorologists.
 
@@
 
-Mark I
+Mark I does not support real-time data acquisition and its processing is limited to an unaveraged power spectrum and range-Doppler plot.
 
 Mark II supports real-time data acquisition (see Sec.
-\ref{sc:AltToDblBuf}) and saving of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}.
-While the data acquisition is real-time, it is not continuous.
+\ref{sc:AltToDblBuf}) and continuous streaming of raw data (\acrshort{ac:adc} integers) to disk, however does not perform any processing beyond a range-Doppler plot for each \acrshort{ac:cpi}.
 
@@
 
+\begin{algorithm}
+	\centering
+	\begin{algorithmic}
+		\For{each \acrshort{ac:cpi} in the frame}
+		\State copy \acrshort{ac:adc} integers (uint16) into buffer (float64)
+		\For{each chirp}
+		\State apply fast-time windowing to chirp samples
+		\EndFor
+		\State execute fast-time \acrshort{ac:fft}
+		\For{each chirp}
+		\For{each range bin in chirp}
+		\State calculate \acrshort{ac:fft} magnitude
+		\State convert to logarithmic scale
+		\State apply fast-time corrections
+		\State apply fast-time windowing correction and \acrshort{ac:fft} normalisation
+		\EndFor
+		\EndFor
+		\For{each column}
+		\State apply slow-time windowing to each range bin
+		\EndFor
+		\State execute slow-time \acrshort{ac:fft}
+		\For{each chirp}
+		\For{each range bin in chirp}
+		\State calculate \acrshort{ac:fft} magnitude
+		\State convert to logarithmic scale
+		\State apply fast-time corrections
+		\State apply slow-time windowing correction and \acrshort{ac:fft} normalisation
+		\State transpose array index and shift so spectrum is centred about DC
+		\EndFor
+		\EndFor
+		\State display processed frame
+		\State swap $A$ and $B$ pointers
+		\EndFor
+	\end{algorithmic}
+	\caption{Key steps in \acrshort{ac:fmcw}-Doppler process.}\label{alg:FMCWProc}
+\end{algorithm}
+
 The window functions available in the new software are flat-top, Hann, Blackman, and Blackman-Harris.
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=\textwidth]{window-none}
-	\caption{Fast-time power spectrum without windowing.}
+	\caption{Averaged fast-time power spectrum of sine wave without windowing.
+Spectral leakage is noticeable at the peak near the \(200\)th range bin.
+The leakage masks aliases from the signal generator.
+Note that the x-axis label is incorrect: it should be the range bin number.}
 	\label{fig:WindowNone}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=\textwidth]{window-bmh}
-	\caption{Fast-time power spectrum with Blackman-Harris windowing.}
+	\caption{Averaged fast-time power spectrum of sine wave with Blackman-Harris windowing applied.
+Spectral leakage is greatly reduced and aliases from the signal generator are no longer obscured.
+Note that the x-axis label is incorrect: it should be the range bin number.}
 	\label{fig:WindowBMH}
@@
 
-\subsection{Averaging}
-How is averaging implemented? Not much to say here really
-
 \section{Results}
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.4\textwidth]{working-cloud_range-doppler}
-	\caption{Screenshot of the new user interface.}
+	\caption{Range-Doppler plot showing a cloud and some precipitation.
+Averaging over \(5\) seconds and Blackman-Harris windowing was applied.
+A hardware issue is visible as a mysterious staircase pattern.}
 	\label{fig:WorkingCloudRangeDoppler}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=\textwidth]{working-cloud_power-spect}
-	\caption{Screenshot of the new user interface.}
+	\caption{Averaged power spectrum of data in \ref{fig:WorkingCloudRangeDoppler}.
+Two small bumps are visible near the \(10\)th and \(95\)th range bins.
+A hardware issue is visible as a series of spikes.}
 	\label{fig:WorkingCloudPowerSpectrum}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-	\includegraphics[width=0.4\textwidth]{working-hail_range-doppler}
-	\caption{Screenshot of the new user interface.}
-	\label{fig:WorkingHailRangeDoppler}
+	\includegraphics[width=\textwidth]{working-cloud_power-spect-unavg}
+	\caption{Unaveraged power spectrum of data in \ref{fig:WorkingCloudRangeDoppler}.}
+	\label{fig:WorkingCloudPowerSpectrumUnaveraged}
 \end{figure}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{working-hail_power-spect}
-	\caption{Screenshot of the new user interface.}
-	\label{fig:WorkingHailPowerSpectrum}
-\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.4\textwidth]{working-heavy-rain-sleet_range-doppler}
-	\caption{Screenshot of the new user interface.}
+	\caption{Range-Doppler plot from the new user interface showing heavy rain.
+Averaging time is \(5\) seconds and Blackman-Harris windowing has been applied.
+Some \acrshort{ac:dc} noise is visible at zero range and zero velocity (bin number \(31\)).}
 	\label{fig:WorkingHeavyRainSnowRangeDoppler}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
 	\includegraphics[width=\textwidth]{working-heavy-rain-sleet_power-spect}
-	\caption{Screenshot of the new user interface.}
+	\caption{Averaged range profile for the same data in Fig. \ref{fig:WorkingHeavyRainSnowRangeDoppler}. The rain is visible as a large bulge between range bins \(1\) and \(150\).}
 	\label{fig:WorkingHeavyRainSnowPowerSpectrum}
@@
 
-\section{Future work}
-\subsection{Calibration}
+\section{Conclusions}
+\subsection{Future work}
+\subsubsection{Calibration}
 Currently the output power is in \(\si{\deci\belm}\) rather than \(\si{\deci\belz}\).
@@
 
-\subsection{Doppler moments}
+\subsubsection{Doppler moments}
 Extracting the Doppler spectrum from the averaged range-Doppler data has already been implemented along with UI controls for displaying Doppler moments, however the results are wildly incorrect.
 
-the formulas used for determining the moments are incorrect.
+\subsubsection{Performance improvements}
+\paragraph{Multithreading.} Many of the calculations in the \acrshort{ac:fmcw}-Doppler process are performed on large arrays.
+Splitting the workload across multiple threads would greatly improve throughput.
+An easy way of parallelising loops with is to use \acrshort{ac:openmp}.
 
-\subsection{Effect of ambient temperature}
-\subsection{NetCDF}
-
-\subsection{Performance improvements}
-\subsubsection{Multithreading}
-Many of the calculations in the \acrshort{ac:fmcw}-Doppler process are highly parallel and are performed on large
-
-An easy way of parallelising loops with is to use \acrshort{ac:openmp}
-
-\subsubsection{SIMD}
-Single instruction, multiple data (\acrshort{ac:simd}) is another type of parallel processing where a single instruction operates simultaneously on multiple pieces of data.
+\paragraph{Single instruction, multiple data} (\acrshort{ac:simd}) is another type of parallel processing where a single instruction operates simultaneously on multiple pieces of data.
 \acrshort{ac:fftw} uses this extensively.
@@
 
-\section{Conclusions}
+\subsection{Adapt code for other radars}
+Both the Mark I and Mark II code exist as a single source file and are heavily tied to \acrshort{ac:cvi} and \acrshort{ac:daq} card library.
+The new code was built with portability and modularity in mind, so each component (data acquisition, \acrshort{ac:fmcw} processing, user interface) is split into its own source file.
+Only the user interface module depends on \acrshort{ac:cvi}.
+
+The two biggest features were successfully implemented: continuous real-time data acquisition and signal averaging.
+Progress was made towards extraction of Doppler moments, however some debugging is required.
+The modular design will allow for easier addition of features and for it to be adapted to other radars.
+The performance improvements mean the code could be used for radars that require fast response times such as drone detection.
 
